% phpMyAdmin LaTeX Dump
% version 4.9.0.1
% https://www.phpmyadmin.net/
%
% Host: localhost
% Gegenereerd op: 09 feb 2021 om 09:49
% Serverversie: 5.7.30-0ubuntu0.18.04.1
% PHP-versie: 7.2.24-0ubuntu0.18.04.4
% 
% Database: 'req_tool'
% 

%
% Structuur: cons_req
%
 \begin{longtable}{|l|c|c|c|l|l|l|} 
 \caption{Structuur van de tabel cons\_req} \label{tab:cons_req-structure} \\
 \hline \multicolumn{1}{|c|}{\textbf{Kolom}} & \multicolumn{1}{|c|}{\textbf{Type}} & \multicolumn{1}{|c|}{\textbf{Leeg}} & \multicolumn{1}{|c|}{\textbf{Standaardwaarde}} & \multicolumn{1}{|c|}{\textbf{Verwijst naar}} & \multicolumn{1}{|c|}{\textbf{Opmerkingen}} & \multicolumn{1}{|c|}{\textbf{MIME}} \\ \hline \hline
\endfirsthead
 \caption{Structuur van de tabel cons\_req (vervolgd)} \\ 
 \hline \multicolumn{1}{|c|}{\textbf{Kolom}} & \multicolumn{1}{|c|}{\textbf{Type}} & \multicolumn{1}{|c|}{\textbf{Leeg}} & \multicolumn{1}{|c|}{\textbf{Standaardwaarde}} & \multicolumn{1}{|c|}{\textbf{Verwijst naar}} & \multicolumn{1}{|c|}{\textbf{Opmerkingen}} & \multicolumn{1}{|c|}{\textbf{MIME}} \\ \hline \hline \endhead \endfoot 
\textbf{\textit{unique\_nr}} & int(11) & Nee &  &  &  &  \\ \hline 
standard & varchar(26) & Ja & NULL &  &  &  \\ \hline 
type\_req & varchar(11) & Ja & NULL &  &  &  \\ \hline 
req\_nr & varchar(9) & Ja & NULL &  &  &  \\ \hline 
description & varchar(682) & Ja & NULL &  &  &  \\ \hline 
mandatory\_l1 & varchar(5) & Ja & NULL &  &  &  \\ \hline 
sec\_class & int(1) & Ja & NULL &  &  &  \\ \hline 
prim\_keyw & varchar(54) & Ja & NULL &  &  &  \\ \hline 
sec\_keyw & varchar(34) & Ja & NULL &  &  &  \\ \hline 
cat\_nr & varchar(6) & Ja & NULL &  &  &  \\ \hline 
iotsfmapetsi & varchar(5) & Ja & NULL &  &  &  \\ \hline 
threats & varchar(167) & Ja & NULL &  &  &  \\ \hline 
remarks & varchar(2954) & Ja & NULL &  &  &  \\ \hline 
ref\_author & varchar(733) & Ja & NULL &  &  &  \\ \hline 
ref\_url & varchar(2088) & Ja & NULL &  &  &  \\ \hline 
licence & varchar(214) & Ja & NULL &  &  &  \\ \hline 
level\_2 & varchar(5) & Ja & NULL &  &  &  \\ \hline 
level\_3 & varchar(5) & Ja & NULL &  &  &  \\ \hline 
 \end{longtable}

%
% Gegevens: cons_req
%
 \begin{longtable}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|} 
 \hline \endhead \hline \endfoot \hline 
 \caption{Inhoud van tabel cons\_req} \label{tab:cons_req-data} \\\hline \multicolumn{1}{|c|}{\textbf{unique\_nr}} & \multicolumn{1}{|c|}{\textbf{standard}} & \multicolumn{1}{|c|}{\textbf{type\_req}} & \multicolumn{1}{|c|}{\textbf{req\_nr}} & \multicolumn{1}{|c|}{\textbf{description}} & \multicolumn{1}{|c|}{\textbf{mandatory\_l1}} & \multicolumn{1}{|c|}{\textbf{sec\_class}} & \multicolumn{1}{|c|}{\textbf{prim\_keyw}} & \multicolumn{1}{|c|}{\textbf{sec\_keyw}} & \multicolumn{1}{|c|}{\textbf{cat\_nr}} & \multicolumn{1}{|c|}{\textbf{iotsfmapetsi}} & \multicolumn{1}{|c|}{\textbf{threats}} & \multicolumn{1}{|c|}{\textbf{remarks}} & \multicolumn{1}{|c|}{\textbf{ref\_author}} & \multicolumn{1}{|c|}{\textbf{ref\_url}} & \multicolumn{1}{|c|}{\textbf{licence}} & \multicolumn{1}{|c|}{\textbf{level\_2}} & \multicolumn{1}{|c|}{\textbf{level\_3}} \\ \hline \hline  \endfirsthead 
\caption{Inhoud van tabel cons\_req (vervolgd)} \\ \hline \multicolumn{1}{|c|}{\textbf{unique\_nr}} & \multicolumn{1}{|c|}{\textbf{standard}} & \multicolumn{1}{|c|}{\textbf{type\_req}} & \multicolumn{1}{|c|}{\textbf{req\_nr}} & \multicolumn{1}{|c|}{\textbf{description}} & \multicolumn{1}{|c|}{\textbf{mandatory\_l1}} & \multicolumn{1}{|c|}{\textbf{sec\_class}} & \multicolumn{1}{|c|}{\textbf{prim\_keyw}} & \multicolumn{1}{|c|}{\textbf{sec\_keyw}} & \multicolumn{1}{|c|}{\textbf{cat\_nr}} & \multicolumn{1}{|c|}{\textbf{iotsfmapetsi}} & \multicolumn{1}{|c|}{\textbf{threats}} & \multicolumn{1}{|c|}{\textbf{remarks}} & \multicolumn{1}{|c|}{\textbf{ref\_author}} & \multicolumn{1}{|c|}{\textbf{ref\_url}} & \multicolumn{1}{|c|}{\textbf{licence}} & \multicolumn{1}{|c|}{\textbf{level\_2}} & \multicolumn{1}{|c|}{\textbf{level\_3}} \\ \hline \hline \endhead \endfoot
1 & ETSI consumer security IoT & requirement & 5.1-1 & All IoT device passwords shall be unique and shall not be resettable to any universal factory default value. & Yes & \textit{NULL} & No universal default passwords & \textit{NULL} & 5.1 & \textit{NULL} & \textit{NULL} & The aim of the above provisions is to ensure that IoT services are kept up and running as the adoption of IoT devices across all aspects of a consumer's life increases, including in functions that are relevant to personal safety. The impact on people's lives could be prevalent if, for example, an internet connection is lost to a connected door and someone is locked outside. Another example is a home heating system that turns off because of a DDoS attack against a cloud service. It is important to note that other safety-related regulations can apply, but the key is to avoid making outages the cause of these problems and to design products and services ready for these challenges. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
2 & ETSI consumer security IoT & requirement & 5.10-1 & If telemetry data is collected from IoT devices and services, such as usage and measurement data, it should be examined for security anomalies. & Yes & \textit{NULL} & Examine system telemetry data & \textit{NULL} & 5.10 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
3 & ETSI consumer security IoT & requirement & 5.10-2 & If telemetry data is collected from IoT devices and services, the processing of personal data should be kept to a minimum and such data should be anonymized. & Yes & \textit{NULL} & Examine system telemetry data & \textit{NULL} & 5.10 & \textit{NULL} & \textit{NULL} & <p>IoT systems and devices are relied upon by consumers for increasingly important use cases that can be safety-relevant or life-impacting. Keeping services running locally if there is a loss of network is one of the measures that can be taken to increase resilience. Other measures can include building redundancy into associated services as well as mitigations against, for example, Distributed Denial of Service (DDoS) attacks or signalling storms which can be caused by massreconnections of devices following an outage. It is expected that the level of resilience necessary is proportionate and determined by usage, with consideration given to others that rely on the system, service or device given that an outage can have a wider impact than expected.\&nbsp;<br></p> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
4 & ETSI consumer security IoT & requirement & 5.10-3 & If telemetry data is collected from IoT devices and services, consumers shall be provided with information on what telemetry data is collected and the reasons for this. & No & \textit{NULL} & Examine system telemetry data & \textit{NULL} & 5.10 & \textit{NULL} & \textit{NULL} & It is expected that the appropriate entity, such as the service provider or device manufacturer, ensures that personal data is processed in accordance with applicable data protection law, for example the GDPR [i.7], and also in accordance with applicable legislation regarding security and regulatory matters. Obtaining consent "in a valid way" normally involves giving consumers a free, obvious and explicit opt-in choice of whether their personal data can be used for a specified purpose. Consumers expect to be provided with means to preserve their privacy by means of configuring IoT device and service functionality appropriately. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
5 & ETSI consumer security IoT & requirement & 5.11-1 & Devices and services should be configured such that personal data can easily be removed from them when there is a transfer of ownership, if the consumer wishes to delete it, if the consumer wishes to remove a service from the device and/or at disposal of the device & No & \textit{NULL} & Make it easy for consumers to delete personal data & \textit{NULL} & 5.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
6 & ETSI consumer security IoT & requirement & 5.11-2 & Consumers should be given clear instructions on how to delete their personal data. & No & \textit{NULL} & Make it easy for consumers to delete personal data & \textit{NULL} & 5.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
7 & ETSI consumer security IoT & requirement & 5.11-3 & Consumers should be provided with clear confirmation that personal data has been deleted from services, devices and applications. & Yes & \textit{NULL} & Make it easy for consumers to delete personal data & \textit{NULL} & 5.11 & \textit{NULL} & \textit{NULL} & The ability to remotely recover from these situations can rely on a known good state, such as locally storing a known good version to enable safe recovery and updating of the device. This will avoid denial of service and costly recalls or maintenance visits, whilst managing the risk of potential takeover of the device by an attacker subverting update or other network communications mechanisms. If an IoT device detects something unusual has happened with its software, it will be able to inform the right person. In some cases, devices can have the ability to be in administration mode - for example, there can be a user mode for a thermostat in a room that prevents other settings being changed. In these cases, an alert to the administrator is appropriate as that person has the ability to act on the alert. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
8 & ETSI consumer security IoT & requirement & 5.12-1 & Installation and maintenance of IoT devices should employ minimal steps and should follow security best practice on usability. Consumers should also be provided with guidance on how to securely set up their device. & Yes & \textit{NULL} & Make installation and maintenance of devices easy & \textit{NULL} & 5.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
9 & ETSI consumer security IoT & requirement & 5.13-1 & Data input via user interfaces and transferred via application programming interfaces (APIs) or between networks in services and devices shall be validated. & Yes & \textit{NULL} & Validate input data & \textit{NULL} & 5.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
10 & ETSI consumer security IoT & requirement & 5.2-1 & Companies that provide internet-connected devices and services shall provide a public point of contact as part of a vulnerability disclosure policy in order that security researchers and others are able to report issues. & Yes & \textit{NULL} & Implement a means to manage reports of vulnerabilities & \textit{NULL} & 5.2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
11 & ETSI consumer security IoT & requirement & 5.2-2 & Disclosed vulnerabilities should be acted on in a timely manner. & Yes & \textit{NULL} & Implement a means to manage reports of vulnerabilities & \textit{NULL} & 5.2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
12 & ETSI consumer security IoT & requirement & 5.2-3 & Companies should continually monitor for, identify and rectify security vulnerabilities within products and services they sell, produce, have produced and services they operate as part of the product security lifecycle. & Yes & \textit{NULL} & Implement a means to manage reports of vulnerabilities & \textit{NULL} & 5.2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
13 & ETSI consumer security IoT & requirement & 5.3-1 & All software components in consumer IoT devices should be securely updateable. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
14 & ETSI consumer security IoT & requirement & 5.3-2 & The consumer should be informed by the appropriate entity, such as the manufacturer or service provider, that an update is required. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & It is expected that products meet the needs of users whilst remaining resilient to attacks on encryption. However,
appropriateness of security controls and the use of encryption is dependent on many factors including the usage context.
As security is ever-evolving it is difficult to give prescriptive advice about encryption measures without the risk of such
advice quickly becoming obsolete. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
15 & ETSI consumer security IoT & requirement & 5.3-3 & When software components are updateable, updates shall be timely. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
16 & ETSI consumer security IoT & requirement & 5.3-4 & When software components are updateable, an end-of-life policy shall be published for devices that explicitly states the minimum length of time for which a device will receive software updates and the reasons for the length of the support period. this & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & Reverse engineering of devices and applications can easily discover credentials such as hard-coded usernames and passwords in software. Simple obfuscation methods also used to obscure or encrypt this hard-coded information can be trivially broken. Secure, trusted storage mechanisms can be used to secure security-sensitive data, such as those provided by a Trusted Execution Environment (TEE) and associated trusted, secure storage, or the secure storage and processing capabilities of software running on a Universal Integrated Circuit Card UICC/embedded Universal Integrated Circuit Card (eUICC). & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
17 & ETSI consumer security IoT & requirement & 5.3-5 & When software components are updateable, the need for each update should be made clear to consumers and an update should be easy to implement. & No & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & There are some situations where devices cannot be patched. For constrained devices a replacement plan needs to be in place and be clearly communicated to the consumer. This plan would typically detail a schedule for when technologies will need to be replaced and, where applicable, when support for hardware and software ends. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
18 & ETSI consumer security IoT & requirement & 5.3-6 & When software components are updateable, updates should, where possible, maintain the basic functioning of the device, which can be critical to remain available during an update. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
19 & ETSI consumer security IoT & requirement & 5.3-7 & When software components are updateable, the provenance of software updates should be assured and security patches should be delivered over a secure channel. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & NOTE 2: Software update mechanisms can present an attack vector. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
20 & ETSI consumer security IoT & requirement & 5.3-8 & For constrained devices that cannot have their software updated, the product should be isolable and the hardware replaceable. & Yes & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & <p>It can be critical for consumers that a device continues to operate during an update. This is why the provision above recommends to "maintain the basic functioning of the device" where possible. </p><p>EXAMPLE: During an update, a watch is expected to continue to tell the time, a home thermostat is expected to continue to be operable and heating settings changeable by users and a smart lock usable for unlocking and locking a door. This can become a critical safety issue for some types of devices and systems if not considered or managed correctly.Particularly, devices that fulfil a safetyrelevant function are expected not to turn completely off in the case of an update; some minimal system functional capability is expected.</p> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
21 & ETSI consumer security IoT & requirement & 5.3-9 & For constrained devices that cannot have their software updated, the rationale for the absence of software updates, the period of hardware replacement support and an end-of-life policy should be published in an accessible way that is clear and transparent to the consumer & No & \textit{NULL} & Keep software updated & \textit{NULL} & 5.3 & \textit{NULL} & \textit{NULL} & <div>Developing and deploying software security updates in a timely manner is one of the most important actions a company</div><div>can take to protect its customers and the wider technical ecosystem. Vulnerabilities often stem from software</div><div>components that are not considered to be security related. It is good practice that all software is kept updated and well</div><div>maintained.</div><div><br></div><div>"Timely" in the context of software updates can vary, depending on the particular issue and fix, as well as other factors,</div><div>such as the ability to reach a device or constrained device considerations. For a non-critical bug, it can be acceptable to</div><div>deliver a software update within a regular patch cycle; for a severe, remote code execution flaw, a more immediate</div><div>update can be expected.</div><div><br></div><div>Software security updates can be provided for devices in a preventative manner, often as part of automatic updates,</div><div>which can remove security vulnerabilities before they are exploited. Managing this can be complex, especially if there</div><div>are parallel cloud service updates, device updates and other service updates to deal with. Therefore, a clear management</div><div>and deployment plan is essential, as is transparency to consumers about the current state of update support.</div><div><br></div><div>In many cases, publishing software updates involves multiple dependencies on other organizations such as</div><div>manufacturers of sub-components, however, this is not a reason to withhold updates. It is essential that the entire</div><div>software supply chain is considered in the development and deployment of security updates.</div><div><br></div><div>Software updates are expected to be provided after the sale of a device and pushed to devices for a period appropriate to</div><div>the device. When purchasing the product, the consumer expects this period of software update support to be made clear.</div><div><br></div><div>Software in consumer IoT devices can be one or more categories (this is a non-exhaustive list): firmware, platform</div><div>software such as an operating system, services and applications. The update process can be different for the different</div><div>categories of software.\&nbsp;</div> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
22 & ETSI consumer security IoT & requirement & 5.5-1 & Security-sensitive data, including any remote management and control, should be encrypted in transit, with such encryption appropriate to the properties of the technology and usage. & No & \textit{NULL} & Communicate securely & \textit{NULL} & 5.5 & \textit{NULL} & \textit{NULL} & <p>\&nbsp;This policy shall be published in an accessible way that is clear and transparent to the
consumer.<br></p> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
23 & ETSI consumer security IoT & requirement & 5.5-2 & All keys should be managed securely. & Yes & \textit{NULL} & Communicate securely & \textit{NULL} & 5.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
24 & ETSI consumer security IoT & requirement & 5.6-1 & Unused software and network ports should be closed. & No & \textit{NULL} & Minimize exposed attack surfaces & \textit{NULL} & 5.6 & \textit{NULL} & \textit{NULL} & <p>NOTE 1: The appropriate entity is decided by the relevant jurisdiction.\&nbsp;<br></p> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
25 & ETSI consumer security IoT & requirement & 5.6-2 & Hardware should not unnecessarily expose access to attack (e.g. open serial access, ports or test points). & Yes & \textit{NULL} & Minimize exposed attack surfaces & \textit{NULL} & 5.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
26 & ETSI consumer security IoT & requirement & 5.6-3 & Software services should not be available if they are not used. & Yes & \textit{NULL} & Minimize exposed attack surfaces & \textit{NULL} & 5.6 & \textit{NULL} & \textit{NULL} & <p>Knowing about a security vulnerability allows companies to respond. Vulnerabilities are expected to be reported
directly to the affected stakeholders in the first instance. If that is not possible vulnerabilities can be reported to national
authorities. Companies are also encouraged to share information with competent industry bodies.</p><p><b>NOTE 1</b>: Competent industry bodies include the GSMA and the IoT Security Foundation. Guidance on
Coordinated Vulnerability Disclosure is available from the IoT Security Foundation which references the
ISO/IEC 29147 standard on vulnerability disclosure [i.4]. The GSMA's industry level Coordinated
Vulnerability Disclosure programme is located at: https://www.gsma.com/cvd.
</p><p><b>Coordinated Vulnerability Disclosure (CVD)</b> is standardized by the International Organization for Standardization
(ISO), is simple to implement and has been proven to be successful in some large software companies around the world
[i.4]. CVD is, however, still not established in the IoT industry and some companies are reticent about dealing with
security researchers. CVD provides a way for security researchers to contact companies to inform them of security
issues putting the company ahead of the threat of malicious exploitation and giving them an opportunity to resolve
vulnerabilities in advance of a public disclosure.</p><p>
Companies that provide internet-connected devices and services have a duty of care to consumers and third parties who
can be harmed by their failure to have a CVD programme in place. Additionally, companies that share this information
through industry bodies can assist others who can be suffering from the same problem.
</p><p>Disclosures can comprise different approaches depending on the circumstances:
</p><ol><li>• Vulnerabilities related to single products or services: the problem is expected to be reported directly to the
affected stakeholder (e.g. device manufacturer, IoT service provider or mobile application developer). The
source of these reports can be security researchers or industry peers.
</li><li>• Systemic vulnerabilities: a stakeholder, such as a device manufacturer, can discover a problem that is
potentially systemic. Whilst fixing it in the device manufacturer's own product is crucial, there is significant
benefit to industry and consumers from sharing this information. Similarly, security researchers can also seek
to report such systemic vulnerabilities. In this case, a relevant competent industry body can coordinate a wider
scale response.</li></ol><p><b style="font-size: 0.875rem;">NOTE 2:</b><span style="font-size: 0.875rem;"> The Common Vulnerability Reporting Framework (CVRF) [i.5] can also be useful to exchange
information on security vulnerabilities.</span></p><p><span style="font-size: 0.875rem;">
Cyber security threat information sharing can support organizations in developing and producing secure products [i.6].\&nbsp;</span></p> & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
27 & ETSI consumer security IoT & requirement & 5.6-4 & Code should be minimized to the functionality necessary for the service/device to operate. & Yes & \textit{NULL} & Minimize exposed attack surfaces & \textit{NULL} & 5.6 & \textit{NULL} & \textit{NULL} & A \&\#34;timely manner\&\#34; for acting on vulnerabilities varies considerably and is incident specific, however, the de facto
standard for the vulnerability process to be completed is within 90 days. A hardware fix can take considerably longer to
address than a software fix. Additionally, a fix that has to be deployed to devices can take time to roll out compared
with a server software fix. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
28 & ETSI consumer security IoT & requirement & 5.6-5 & Software should run with least necessary privileges, taking account of both security and functionality. & No & \textit{NULL} & Minimize exposed attack surfaces & \textit{NULL} & 5.6 & \textit{NULL} & \textit{NULL} & no remarks & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
29 & ETSI consumer security IoT & requirement & 5.7-1 & Software on IoT devices should be verified using secure boot mechanisms, which require a hardware root of trust. & Yes & \textit{NULL} & Ensure software integrity & \textit{NULL} & 5.7 & \textit{NULL} & \textit{NULL} & Systems can be subverted by incorrectly formatted data or code transferred across different types of interface. Automated tools are often employed by attackers in order to exploit potential gaps and weaknesses that emerge as a result of not validating data. Examples include, but are not limited to, data that is: i) Not of the expected type, for example executable code rather than user inputted text. ii) Out of range, for example a temperature value which is beyond the limits of a sensor. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
30 & ETSI consumer security IoT & requirement & 5.7-21 & If an unauthorized change is detected to the software, the device should alert the consumer and/or administrator to an issue and should not connect to wider networks than those necessary to perform the alerting function. & No & \textit{NULL} & Ensure software integrity & \textit{NULL} & 5.7 & \textit{NULL} & \textit{NULL} & Security issues caused by consumer confusion or misconfiguration can be reduced and sometimes eliminated by properly addressing complexity and poor design in user interfaces. Clear guidance to users on how to configure devices securely can also reduce their exposure to threats. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
31 & ETSI consumer security IoT & requirement & 5.8-1 & Device manufacturers and service providers shall provide consumers with clear and transparent information about how their personal data is being used, by whom, and for what purposes, for each device and service. This also applies to third parties that ca & No & \textit{NULL} & \textit{NULL} & \textit{NULL} & 5.8 & \textit{NULL} & \textit{NULL} & IoT devices often change ownership and will eventually be recycled or disposed of. Mechanisms can be provided that allow the consumer to remain in control and remove personal data from services, devices and applications. When a consumer wishes to completely remove their personal data, they also expect this to include backup copies that the service provider may hold. Deleting personal data from a device or service is not simply achieved by resetting a device back to its factory settings. There are many use cases where the consumer is not the owner of a device, but wishes to delete their own personal data from the device and all associated services such as cloud services or mobile applications. EXAMPLE: A user can have temporary usage of consumer IoT products within a rented apartment. Carrying out a factory reset of the product can remove configuration settings or disable the device to the detriment of the apartment owner and a future user. It would be an inappropriate technical mechanism to delete all personal data in this context. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
32 & ETSI consumer security IoT & requirement & 5.8-21 & Where personal data is processed on the basis of consumers' consent, this consent shall be obtained in a valid way. & No & \textit{NULL} & \textit{NULL} & \textit{NULL} & 5.8 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
33 & ETSI consumer security IoT & requirement & 5.8-3 & Consumers who gave consent for the processing of their personal data shall be given the opportunity to withdraw it at any time. & No & \textit{NULL} & \textit{NULL} & \textit{NULL} & 5.8 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
34 & ETSI consumer security IoT & requirement & 5.9-1 & Resilience should be built in to IoT devices and services where required by their usage or by other relying systems, taking into account the possibility of outages of data networks and power. & Yes & \textit{NULL} & Make systems resilient to outages & \textit{NULL} & 5.9 & \textit{NULL} & \textit{NULL} & Examining telemetry, including log data, is useful for security evaluation and allows for unusual circumstances to be identified early and dealt with, minimizing security risk and allowing quick mitigation of problems. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
35 & ETSI consumer security IoT & requirement & 5.9-2 & As far as reasonably possible, IoT services should remain operating and locally functional in the case of a loss of network and should recover cleanly in the case of restoration of a loss of power. & Yes & \textit{NULL} & Make systems resilient to outages & \textit{NULL} & 5.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
36 & ETSI consumer security IoT & requirement & 5.9-3 & Devices should be able to return to a network in an expected, operational and stable state and in an orderly fashion, rather than in a massive-scale reconnect. & No & \textit{NULL} & Make systems resilient to outages & \textit{NULL} & 5.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
37 & ETSI consumer security IoT & requirement & 5.4-1 & Credentials and security-sensitive data shall be stored securely within services and on devices. Hard-coded credentials in device software shall not be used. & Yes & \textit{NULL} & Securely store credentials and security-sensitive data & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & Many IoT devices are being sold with universal default usernames and passwords (such as \&\#34;admin, admin\&\#34;) for user
interfaces through to network protocols. This has been the source of many security issues in IoT and the practice needs
to be discontinued. Following best practice on passwords and other authentication methods is encouraged. Device
security can further be strengthened by having unique and immutable identities.
For guidance see, for example, the NIST Special Publication on Digital Identity Guidelines,
Authentication and Lifecycle Management [i.3]. & ETSI TS 103 645 V1.1.1 (2019-02) Cyber Security for Consumer Internet of Things & https://www.etsi.org/deliver/etsi\_en/303600\_303699/303645/02.01.01\_60/en\_303645v020101p.pdf & No part may be reproduced or utilized in any form or by any means, electronic or mechanical, including photocopying and microfilm except as authorized by written permission of ETSI. © ETSI 2019. All rights reserved & \textit{NULL} & \textit{NULL} \\ \hline 
38 & ENISA Industry 4.0 & requirement & GP-TM-47 & If possible, limit the number of protocols implemented within a given environment to ensure manageability of the system. Also, disable all unused default network services. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking
Physical attacks
Outages & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
Security Guidance for Early Adopters of the Internet of Things
Internet of Things (IoT) Security and Privacy Recommendations
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-3-3:2013 System security requirements and security levels
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns & Siemens
Cloud Security Alliance
BITAG (Broadband Internet Technical Advisory Group)
NIST
IEC
SANS Institute & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7033
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
39 & ENISA Industry 4.0 & requirement & GP-OP-10 & Define cyber incidents relevant for your organisation based on the company's area and range of operation. Classify these incidents according to applicable standards, e.g. by grouping them based on utilisation of a common attack vector (removable media, email, website, etc.) or according to their impact (on organisation's operation, on data, etc.). & \textit{NULL} & \textit{NULL} & II. Organizational practices & Incidents handling & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800-61r2: Computer Security Incident Handling Guide - Recommendations of the National Institute of Standards and Technology
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Identity and Access Management for the Internet of Things - Summary Guidance
Internet of Things Security Guidelines v1.2
Security capabilities supporting safety of the Internet of things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use & IEC
IEC
NIST
NIST
Symantec
NIST
Cloud Security Alliance
IoT Alliance Australia
International Telecommunications Union
NIST
IIC (Industrial Internet Consortium) & https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/specialpublications/nist.sp.800-61r2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
40 & ENISA Industry 4.0 & requirement & GP-TM-39 & In case of extensive and diversified networks with a large number of devices, adopt the Privilege Access Management (PAM) solution to manage elevated privileges (i.e. administrator privileges) in an orderly manner. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental) & Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & Cloud Security Alliance
Cloud Security Alliance
NIST
ISO
IEC & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
41 & ENISA Industry 4.0 & requirement & GP-OP-05 & During the handover phase of the project implementation process, properly build and transfer all cybersecurity documentation, processes and procedures. Within the documentation, include a list of system and service accounts, security logs, response plans, confirmation of all software and firmware versions, up-to-date network diagrams, system architecture, risk register and security limitations. Processes should comprise maintenance routines, anti-virus deployment and assurance, patching processes and accounts' management and authentication processes. Procedures should include firewalls baseline configurations, management and monitoring, change control and fall-over testing. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Endpoints lifecycle & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions
Legal & NIST SP 800-52 r1: Guidelines for the Selection, Configuration, and Use of Transport Layer Security (TLS) Implementations
Cybersecurity for Smart Manufacturing
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security & NIST
NIST
IIC (Industrial Internet Consortium)
ISO
NIST
NIST & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-52r1.pdf
https://www.nist.gov/sites/default/files/documents/2016/12/05/cybersecurity\_for\_smart\_manufacturing.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
42 & ENISA Industry 4.0 & requirement & GP-TM-31 & For control systems which cannot be updated (e.g. legacy systems), apply compensating measures, such as network segmentation, micro segmentation, system relocation or additional real-time monitoring tools. & \textit{NULL} & \textit{NULL} & III. Technical practices & Software/Firmware updates & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Connected Consumer Products. Best Practice Guidelines
Framework for Improving Critical Infrastructure Cybersecurity V1.1
NIST SP 800-52 r1: Guidelines for the Selection, Configuration, and Use of Transport Layer Security (TLS) Implementations
IIC Endpoint Security Best Practices
Industrial Internet of Things Volume G4: Security Framework
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & IoT Security Foundation
NIST
NIST
IIC (Industrial Internet Consortium)
IIC (Industrial Internet Consortium)
GSMA (Global System for Mobile Communications) & https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/CSWP/NIST.CSWP.04162018.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-52r1.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
43 & ENISA Industry 4.0 & requirement & GP-TM-41 & Ensure security of communications channels related to IIoT solutions. Encrypt communications in case of important data (e.g. configuration, personal data, data for control purposes), where it is possible to do so without affecting safety, availability and performance. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking & IoT Security Guidance
Internet of Things (IoT) Security and Privacy Recommendations
Security Guidance for Early Adopters of the Internet of Things
GSMA CLP.14 IoT Security Guidelines for Network Operators
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Internet of Things Security Guidelines v1.2
Security capabilities supporting safety of the Internet of things
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & OWASP (Open Web Application Security Project)
BITAG (Broadband Internet Technical Advisory Group)
Cloud Security Alliance
GSMA (Global System for Mobile Communications)
NIST
OpenAI and others
IoT Alliance Australia
International Telecommunications Union
IoT Security Foundation
IIC (Industrial Internet Consortium)
NIST
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.gsma.com/iot/wp-content/uploads/2017/10/CLP.14-v2.0.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
44 & ENISA Industry 4.0 & requirement & GP-TM-05 & Ensure production data integrity through utilisation of appropriate cryptographic mechanisms and key storage tailored to processing capabilities of the implemented solutions. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & Symantec
IEC
Huawei
NIST
NIST
NIST
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
45 & ENISA Industry 4.0 & requirement & GP-TM-37 & Avoid using shared accounts for access to IIoT devices and systems. Create individual accounts for every user whenever possible, as this will enable tracking of the performed actions to a specific person. If shared accounts are used, change passwords periodically (e.g. every 90 days) and in case of personnel changes within a shared account group (e.g. when an employee leaves). Also, consider deployment of additional compensating controls (e.g. segregation of duties, real-time monitoring tools such as industrial IDS). & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Physical attacks
Unintentional damages (accidental) & Industrie 4.0 Security Guidelines Recommendations for actions
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & VDMA
ISO
ISO
IEC
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & http://www.vdmashop.de/refs/Leitf\_I40\_Security\_En\_LR\_neu.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
46 & ENISA Industry 4.0 & requirement & GP-OP-27 & Clearly define all relevant aspects of the partnership with Third Parties, including security, within the appropriate agreements and contracts (e.g. SLA - service level agreement, NDA - Non-Disclosure Agreements). Sign these agreements and contracts before the start of cooperation. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Third Party Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental)
Failures / Malfunctions
Legal & INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector
Automotive Cybersecurity Best Practices - Executive Summary
IEEE Std 802.1X-2010 - Port-Based Network Access Control
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & ECSO (European Cyber Security Organization)
Auto ISAC (Automotive Information Sharing and Analysis Center)
IEEE
NIST
Cloud Security Alliance
IIC (Industrial Internet Consortium)
ISO
NIST
ISO
IEC
NIST & http://ecs-org.eu/documents/publications/5ad7268b92497.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
http://moodle.eece.cu.edu.eg/pluginfile.php/1799/mod\_folder/content/1/802.1X-2010.pdf?forcedownload=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
47 & ENISA Industry 4.0 & requirement & GP-TM-29 & Perform deployment of patches for the IIoT devices only after proving that no negative consequences exist. Test the patches in a test environment before implementing them in production. If this is not possible, begin with deploying patches only on a segment of a system, ensuring that other zones will continue to operate normally in case a patch exerts any negative impact on a chosen segment. & \textit{NULL} & \textit{NULL} & III. Technical practices & Software/Firmware updates & \textit{NULL} & \textit{NULL} & Failures / Malfunctions & Strategic Principles for Securing the Internet of Things
Connected Consumer Products. Best Practice Guidelines
Hippocratic Oath for Connected Medical Devices
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security Maturity Model: Description and Intended Use & Homeland Security
IoT Security Foundation
The Cavalry
NIST
Cloud Security Alliance
IIC (Industrial Internet Consortium)
NIST
ISO
IIC (Industrial Internet Consortium) & https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iamthecavalry.org/wp-content/uploads/2016/01/I-Am-The-Cavalry-Hippocratic-Oath-for-Connected-Medical-Devices.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
48 & ENISA Industry 4.0 & requirement & GP-TM-33 & Ensure minimal level of authentication security for the IIoT devices and systems. In a segmented network/system, ensure that authorisation only allows for access to a certain segment and no other parts of the system. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental) & IoT Security Guidance
Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
Industry 4.0: Secure by design
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
IoT Security Maturity Model: Description and Intended Use & OWASP (Open Web Application Security Project)
Cloud Security Alliance
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
VDC
ISO
IEC
Huawei
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
49 & ENISA Industry 4.0 & requirement & GP-PS-17 & Avoid the usage of removable devices and disable USB ports (or technically restrict use of removable media on USB ports) if there is no accepted business requirement. At least scan the removable media devices using malware detection software with up-to-date definitions if they need to be connected to the environment. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental) & NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
Industrial Internet of Things Volume G4: Security Framework
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Putting Industrial Cyber Security at the top of the CEO agenda
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & NIST
IIC (Industrial Internet Consortium)
NIST
Siemens
NIST
LNS
ISO
IEC
IEC
GSMA (Global System for Mobile Communications)
NIST & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
50 & ENISA Industry 4.0 & requirement & GP-PS-13 & In complex industrial environments with legacy system asset discovery, use passive monitoring devices instead of active monitoring solutions. It is advisable to utilise passive automatic tools whenever it is feasible, as they do not disrupt systems operation. Utilisation of active monitoring devices can cause adverse effects on the OT environment and disrupt the production process. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Industrial Internet of Things Volume G4: Security Framework
Security Guidance for Early Adopters of the Internet of Things
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security & IIC (Industrial Internet Consortium)
Cloud Security Alliance
IEC
Huawei
IEC
NIST & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
51 & ENISA Industry 4.0 & requirement & GP-OP-22 & Train users of IIoT on the secure usage of their devices. During training sessions, explain to the IIoT users all of the technologies deployed to protect IIoT devices and the ecosystem where the solution is deployed. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Training and Awareness & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Unintentional damages (accidental) & Identity and Access Management for the Internet of Things - Summary Guidance
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & Cloud Security Alliance
NIST
NIST
Cloud Security Alliance
ISO
IEC & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
52 & ENISA Industry 4.0 & requirement & GP-TM-44 & Isolate safety networks from business and control networks. If this is not possible due to business requirements, ensure that solutions for network traffic filtering are in place. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Recommended Practice: Improving Industrial Control System Cybersecurity with Defense-in-Depth Strategies
IEC 62443-1-1:2009 Terminology, concepts and models
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
Industrial Internet of Things Volume G4: Security Framework
Security capabilities supporting safety of the Internet of things
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Homeland Security
IEC
IEC
IEC
IIC (Industrial Internet Consortium)
International Telecommunications Union
NIST
NIST & https://ics-cert.us-cert.gov/sites/default/files/recommended\_practices/NCCIC\_ICS-CERT\_Defense\_in\_Depth\_2016\_S508C.pdf
https://webstore.iec.ch/publication/7029
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
53 & ENISA Industry 4.0 & requirement & GP-TM-52 & Perform periodic reviews of access control privileges and asset configurations at least annually and in case of a major change in the system. & \textit{NULL} & \textit{NULL} & III. Technical practices & Monitoring and auditing & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IoT Security Guidance
NISTIR 8200: Interagency Report on Status of International Cybersecurity Standardization for the Internet of Things (IoT)
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security White Paper 2017
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & NIST
OWASP (Open Web Application Security Project)
NIST
NIST
ENISA
IIC (Industrial Internet Consortium)
ISO
NIST
ISO
Huawei
NIST & https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://csrc.nist.gov/publications/detail/nistir/8200/draft
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
54 & ENISA Industry 4.0 & requirement & GP-PS-20 & Establish risk and threat management process according to the individual needs and security requirements of your company. It should consist of security risk assessment to identify critical security assets and threat modelling to identify security risks and mitigations.D23 & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 30r1 - Guide for Conducting Risk Assessments
Automotive Cybersecurity Best Practices - Executive Summary
IEC 62443-4-1:2013 Secure product development lifecycle requirements
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Internet of Things Security Guidelines v1.2
Putting Industrial Cyber Security at the top of the CEO agenda
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
NIST
Auto ISAC (Automotive Information Sharing and Analysis Center)
IEC
NIST
IIC (Industrial Internet Consortium)
NIST
Symantec
IoT Alliance Australia
LNS
IEC
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-30r1.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://webstore.iec.ch/publication/33615
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
55 & ENISA Industry 4.0 & requirement & GP-OP-03 & Consider security aspects during whole procurement process defining security measures and requirements tailored to particular devices/solutions. The security subject matter expert shall participate during offers revision. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Endpoints lifecycle & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Outages
Disasters & Industrial Internet of Things Volume G4: Security Framework
Security Challenges on the Way Towards Smart Manufacturing
Best practices in cyber supply chain risk management. Smart Manufacturing The Future of Manufacturing and Value Chain Competitiveness
NIST SP 800-52 r1: Guidelines for the Selection, Configuration, and Use of Transport Layer Security (TLS) Implementations
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & IIC (Industrial Internet Consortium)
IoT Security Foundation
NIST
NIST
OWASP (Open Web Application Security Project)
NIST
Cloud Security Alliance
NIST
ISO
IEC
GSMA (Global System for Mobile Communications) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://www.nist.gov/sites/default/files/documents/itl/csd/NIST\_USRP-SmartManu-Cyber-SCRM-Case-Study.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-52r1.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
56 & ENISA Industry 4.0 & requirement & GP-TM-30 & Allow Third Parties to perform patching only if they guarantee and are able to prove that the patch has been tested and will not have any negative consequences on the device or if the Third Party assumes the liability for the update according to an applicable agreement. & \textit{NULL} & \textit{NULL} & III. Technical practices & Software/Firmware updates & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental)
Failures / Malfunctions & Connected Consumer Products. Best Practice Guidelines
Establishing Principles for IoT Security
Hippocratic Oath for Connected Medical Devices
Framework for Improving Critical Infrastructure Cybersecurity V1.1 & IoT Security Foundation
IoT Security Foundation
The Cavalry
NIST & https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2015/09/IoTSF-Establishing-Principles-for-IoT-Security-Download.pdf
https://www.iamthecavalry.org/wp-content/uploads/2016/01/I-Am-The-Cavalry-Hippocratic-Oath-for-Connected-Medical-Devices.pdf
https://nvlpubs.nist.gov/nistpubs/CSWP/NIST.CSWP.04162018.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
57 & ENISA Industry 4.0 & requirement & GP-OP-02 & Take into account security considerations throughout the whole supply chain. Monitor software, hardware and its components throughout the supply chain to detect and prevent unauthorised changes, e.g. introduction of malware to the software. Create unique device identity and maintain it over the lifecycle of the device. Integrity may be verified based on roots of trust, digital signatures and embedded identifiers. Ensure that the integrity of the manufactured device can be measured and attested. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Endpoints lifecycle & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & Industrial Internet of Things Volume G4: Security Framework
Security Challenges on the Way Towards Smart Manufacturing
Best practices in cyber supply chain risk management. Smart Manufacturing The Future of Manufacturing and Value Chain Competitiveness
Avoiding the internet of insecure industrial things
Internet of Things (IoT) Security and Privacy Recommendations
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Security Guidance for Early Adopters of the Internet of Things
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Internet of Things Security Guidelines v1.2
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
IoT Security Foundation
NIST
Elsevier
BITAG (Broadband Internet Technical Advisory Group)
NIST
OpenAI and others
Cloud Security Alliance
Symantec
IoT Alliance Australia
NIST
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://www.nist.gov/sites/default/files/documents/itl/csd/NIST\_USRP-SmartManu-Cyber-SCRM-Case-Study.pdf
https://ac.els-cdn.com/S0267364917303217/1-s2.0-S0267364917303217-main.pdf?\_tid=spdf-11af005b-d10d-44ae-8844-412ab62296e5\&acdnat=1519918986\_1591e0b39b9692d0405b94c67b808d4d
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
58 & ENISA Industry 4.0 & requirement & GP-TM-22 & Protect data at rest (both in volatile and non-volatile memory), in transit and in use. & \textit{NULL} & \textit{NULL} & III. Technical practices & Data protection & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
SCADA And Mobile Security In The Internet Of Things Era
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & NIST
IIC (Industrial Internet Consortium)
OWASP (Open Web Application Security Project)
NIST
ENISA
Cloud Security Alliance
IoT Alliance Australia
IIC (Industrial Internet Consortium)
IEC
Huawei
NIST
IOActive, Embedi
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium)
NIST & https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://ioactive.com/pdfs/SCADA-and-Mobile-Security-in-the-IoT-Era-Embedi-FINALab\%20(1).pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
59 & ENISA Industry 4.0 & requirement & GP-TM-32 & Segregate remote access, i.e. develop a set of rules for control of the remote communication. Limit remote access only to the required systems and monitor it. Ensure full traceability and accountability of the users. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental)
Failures / Malfunctions & IoT Security Guidance
Smart Manufacturing General security and privacy principles to ensure a Trusted IoT environment
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Internet of Things Security Guidelines v1.2
Security capabilities supporting safety of the Internet of things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & OWASP (Open Web Application Security Project)
VDMA
NIST
IIC (Industrial Internet Consortium)
NIST
IoT Alliance Australia
International Telecommunications Union
NIST
ISO
ISO
IEC
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications)
NIST & https://www.owasp.org/index.php/IoT\_Security\_Guidance
http://ec.europa.eu/information\_society/newsroom/image/document/2017-11/smart\_manufacturing\_to\_ensure\_a\_trusted\_iot\_environment\_by\_vdma\_0B8285E7-9C90-7E5C-04DA25B61A5C3FA5\_43660.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
60 & ENISA Industry 4.0 & requirement & GP-TM-06 & Monitor the production data at rest and in transit to identify potential unauthorised data modification. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems & Siemens
IEC
Huawei
NIST
NIST
NIST
GSMA (Global System for Mobile Communications) & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
61 & ENISA Industry 4.0 & requirement & GP-TM-56 & Implement and document changes in configuration according to a change management policy developed by the organisation based on risk analysis. This policy should include responsibility (i.e. system owner, approvers, etc.) and security aspects. The business owners of assets should accept it. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental) & Accompanying the Industrial Internet of Things Volume G1: Reference architecture
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & IIC (Industrial Internet Consortium)
NIST
NIST
IIC (Industrial Internet Consortium)
ISO
NIST
ISO
IEC
IEC
SANS Institute
NIST & https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://webstore.iec.ch/publication/7030
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
62 & ENISA Industry 4.0 & requirement & GP-TM-18 & Store long-term service-layer keys (other than public keys) in a server-HSM residing in infrastructure equipment. The HSM containing the M2M long-term service keys should be bound to the M2M Device or M2M Gateway, using physical and/or logical means. & \textit{NULL} & \textit{NULL} & III. Technical practices & Machine-to-Machine security & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking & Hardware-based solutions secure machine identities in smart factories
TR 0008 Security V2.0.0 - Security. Technical Report
IIC Endpoint Security Best Practices
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
IEC 62443-3-3:2013 System security requirements and security levels
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems & Infineon
oneM2M
IIC (Industrial Internet Consortium)
IoT Security Foundation
IIC (Industrial Internet Consortium)
IEC
GSMA (Global System for Mobile Communications) & https://www.infineon.com/dgdl/Infineon-IoT+Security+in+Smart+Factories-ART-v01\_00-EN.pdf?fileId=5546d46254e133b40154e22c8a7d0251
http://www.onem2m.org/images/files/deliverables/Release2/TR-0008-Security-V2\_0\_0.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://webstore.iec.ch/publication/7033
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
63 & ENISA Industry 4.0 & requirement & GP-OP-08 & Within the Security Architecture, allocate and distribute clear roles and responsibilities for security between IT, Engineering/Automation and Operations departments. Clearly define and communicate roles for both OT systems and security processes. & \textit{NULL} & \textit{NULL} & II. Organizational practices & IT Security architecture & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Unintentional damages (accidental)
Failures / Malfunctions & Accompanying the Industrial Internet of Things Volume G1: Reference architecture
Building the New Network Security Architecture for the Future
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
ANSI/ISA-95 Part 1: Models and Terminology
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
SANS Institute
IIC (Industrial Internet Consortium)
ISO
ISO
ISA
IEC
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
64 & ENISA Industry 4.0 & requirement & GP-TM-26 & Anonymise any direct or indirect personal data processed within the company system (e.g. names of system operators and information on their performance), having considered all relevant legal requirements, or properly secure it, e.g. through role-based access control and encryption. & \textit{NULL} & \textit{NULL} & III. Technical practices & Data protection & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Identity and Access Management for the Internet of Things - Summary Guidance
IoT Security Guidance
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.11 IoT Security Guidelines Overview Document
IoT Security Maturity Model: Description and Intended Use & Cloud Security Alliance
OWASP (Open Web Application Security Project)
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
Huawei
IEC
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium) & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
65 & ENISA Industry 4.0 & requirement & GP-TM-12 & Focus on ensuring the resilience of Industry 4.0 systems by creating a business continuity plan (BCP) and disaster recovery plan (DRP). Ensure continuity of the systems operation even in the event of security incidents. Perform periodic testing of the plans and adapt them according to lessons learnt from tests and actual security incidents. & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & BSI-Standards 100-4 - Business Continuity Management
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST Advanced Manufacturing Series 300-1 Reference Architecture for Smart Manufacturing Part 1: Functional Models
Industrial Internet of Things Volume G4: Security Framework
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Internet of Things Security Guidelines v1.2
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & Federal Office for Information Security (BSI)
NIST
NIST
IIC (Industrial Internet Consortium)
NIST
IoT Alliance Australia
ISO
NIST
IEC
IIC (Industrial Internet Consortium) & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-4\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ams/NIST.AMS.300-1.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
66 & ENISA Industry 4.0 & requirement & GP-PS-21 & Perform risk analysis which includes cybersecurity aspects at least annually. Also, integrate it with other processes, such as change management, incident handling and vulnerability management in order to ensure that risk analysis is performed & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 30r1 - Guide for Conducting Risk Assessments
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Vulnerability Management: Tools, Challenges and Best Practices
Putting Industrial Cyber Security at the top of the CEO agenda
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use
GSMA CLP.11 IoT Security Guidelines Overview Document & IIC (Industrial Internet Consortium)
NIST
NIST
SANS Institute
LNS
NIST
IEC
IIC (Industrial Internet Consortium)
GSMA (Global System for Mobile Communications) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-30r1.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
67 & ENISA Industry 4.0 & requirement & GP-TM-57 & Develop a dedicated procedure for impact analysis. Before implementation of change in the system, perform an analysis to determine the criticality of the considered change. Test changes to the configuration that may exert an impact on operations and precede them with risk analysis. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental) & NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ANSI/ISA-95 Part 1: Models and Terminology
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & NIST
IIC (Industrial Internet Consortium)
NIST
ISO
ISA
IEC & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54534.html
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
68 & ENISA Industry 4.0 & requirement & GP-OP-25 & Do not provide a direct connection for the vendor to a system in a control or production layer. Support security of remote access with network segmentation, VLANS configuration, implemented firewalls and network traffic filtering. Allow only for access to the selected necessary functions and parts of the network (the rule of least privilege should be in place). & \textit{NULL} & \textit{NULL} & II. Organizational practices & Third Party Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental)
Failures / Malfunctions & INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector
Automotive Cybersecurity Best Practices - Executive Summary
Industrial Internet of Things Volume G4: Security Framework
Framework for Cyber-Physical Systems: Volume 1, Overview
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Internet of Things Security Guidelines v1.2
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & ECSO (European Cyber Security Organization)
Auto ISAC (Automotive Information Sharing and Analysis Center)
IIC (Industrial Internet Consortium)
NIST
NIST
IoT Alliance Australia
NIST & http://ecs-org.eu/documents/publications/5ad7268b92497.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.1500-201.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
69 & ENISA Industry 4.0 & requirement & GP-TM-02 & Authorise all IIoT devices within the OT network utilising the appropriate methods, e.g. digital certificates/PKI. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Accompanying the Industrial Internet of Things Volume G1: Reference architecture
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
Internet of Things Security Guidelines v1.2
Security capabilities supporting safety of the Internet of things
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
Industry 4.0: Secure by design
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & IIC (Industrial Internet Consortium)
NIST
NIST
IIC (Industrial Internet Consortium)
IoT Alliance Australia
International Telecommunications Union
IoT Security Foundation
IIC (Industrial Internet Consortium)
VDC
Huawei
IEC
IEC
NIST
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
70 & ENISA Industry 4.0 & requirement & GP-PS-06 & Address privacy-related issues based on applicable local and international regulations, such as The General Data Protection Regulation (GDPR). & \textit{NULL} & \textit{NULL} & I. Policies & Privacy by design & \textit{NULL} & \textit{NULL} & Legal & The General Data Protection Regulation (GDPR) (EU) 2016/679
Security Guidance for Early Adopters of the Internet of Things
Internet of Things (IoT) Security Best Practices
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
Identity and Access Management for the Internet of Things - Summary Guidance
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.11 IoT Security Guidelines Overview Document
IoT Security Maturity Model: Description and Intended Use & European Parliament and Council of the European Union
Cloud Security Alliance
IEEE
World Economic Forum
Cloud Security Alliance
IoT Security Foundation
IIC (Industrial Internet Consortium)
NIST
ISO
Huawei
IEC
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium) & https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=uriserv:OJ.L\_.2016.119.01.0001.01.ENG
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://internetinitiative.ieee.org/images/files/resources/white\_papers/internet\_of\_things\_feb2017.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
71 & ENISA Industry 4.0 & requirement & GP-OP-17 & Establish a comprehensive and well-defined process for disclosure of vulnerabilities. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Vulnerabilities management & \textit{NULL} & \textit{NULL} & Failures / Malfunctions & Internet of Things (IoT) Security Best Practices
GSMA CLP.11 IoT Security Guidelines Overview Document
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Strategic Principles for Securing the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations & IEEE
GSMA (Global System for Mobile Communications)
NIST
NIST
OpenAI and others
ENISA
Cloud Security Alliance
IoT Alliance Australia
Homeland Security
NIST & https://internetinitiative.ieee.org/images/files/resources/white\_papers/internet\_of\_things\_feb2017.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
72 & ENISA Industry 4.0 & requirement & GP-TM-48 & Ensure a secure environment for key exchange and key management while avoiding sharing cryptographic keys across multiple devices. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking & IoT Security Guidance
Internet of Things (IoT) Security and Privacy Recommendations
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Connected Consumer Products. Best Practice Guidelines
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security White Paper 2017
GSMA CLP.14 IoT Security Guidelines for Network Operators
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & OWASP (Open Web Application Security Project)
BITAG (Broadband Internet Technical Advisory Group)
Cloud Security Alliance
NIST
IoT Security Foundation
ISO
Huawei
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iso.org/standard/54533.html
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2017/10/CLP.14-v2.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
73 & ENISA Industry 4.0 & requirement & GP-TM-28 & Execute automatic update procedures only if they are based on the risk analysis and if the devices for which the automatic update can be allowed are identified. Verify the source of the update. & \textit{NULL} & \textit{NULL} & III. Technical practices & Software/Firmware updates & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Physical attacks & Strategic Principles for Securing the Internet of Things
Hippocratic Oath for Connected Medical Devices
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
IIC Endpoint Security Best Practices
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Identity and Access Management for the Internet of Things - Summary Guidance
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls & Homeland Security
The Cavalry
Siemens
IIC (Industrial Internet Consortium)
NIST
Cloud Security Alliance
IIC (Industrial Internet Consortium)
ISO & https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://www.iamthecavalry.org/wp-content/uploads/2016/01/I-Am-The-Cavalry-Hippocratic-Oath-for-Connected-Medical-Devices.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54533.html & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
74 & ENISA Industry 4.0 & requirement & GP-OP-01 & Focus on the security of software and hardware during every stage of the endpoint lifecycle. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Endpoints lifecycle & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Legal & Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
IoT Security White Paper 2017
Industrie 4.0 Security Guidelines Recommendations for actions
Managing security, safety and privacy in Smart Factories
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
Putting Industrial Cyber Security at the top of the CEO agenda
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
Security Analysis of Zigbee
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & World Economic Forum
Huawei
VDMA
Smart Factory Innovation Forum
NIST
NIST
Cloud Security Alliance
IoT Alliance Australia
IIC (Industrial Internet Consortium)
LNS
ISO
MIT
IEC
IEC
NIST
GSMA (Global System for Mobile Communications) & http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
http://www.vdmashop.de/refs/Leitf\_I40\_Security\_En\_LR\_neu.pdf
https://www.pinsentmasons.com/dokument/it-security-in-smart-factories-white-paper-april-2015.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.iso.org/standard/54533.html
https://courses.csail.mit.edu/6.857/2017/project/17.pdf
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
75 & ENISA Industry 4.0 & requirement & GP-PS-08 & Establish the physical location of data stored by the organisation and define between which organisations data will be transferred. Restrict access to collected personal data only to authorised individuals. Periodically revise access rights and terminate them as soon as possible after an employee's change of position/leaving company. & \textit{NULL} & \textit{NULL} & I. Policies & Privacy by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Physical attacks
Legal & Security Guidance for Early Adopters of the Internet of Things
ETSI TR 103 375 SmartM2M; IoT Standards landscape and future evolutions
ANSI/ISA-95 Part 1: Models and Terminology
IoT Security Guidance
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Identity and Access Management for the Internet of Things - Summary Guidance
Industrial Internet of Things Volume G4: Security Framework
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
ETSI (European Telecommunications Standards Institute)
ISA
OWASP (Open Web Application Security Project)
NIST
Cloud Security Alliance
IIC (Industrial Internet Consortium)
IEC
NIST
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.etsi.org/deliver/etsi\_tr/103300\_103399/103375/01.01.01\_60/tr\_103375v010101p.pdf
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
76 & ENISA Industry 4.0 & requirement & GP-OP-26 & Prompt suppliers for information on the security of their processes and commitments to the product they deliver, e.g. by preparing a questionnaire for suppliers regarding their security contributions to the items they deliver and select partners taking into account its results. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Third Party Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental)
Failures / Malfunctions & INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector
Automotive Cybersecurity Best Practices - Executive Summary
Industrial Internet of Things Volume G4: Security Framework
Security Challenges on the Way Towards Smart Manufacturing
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Strategic Principles for Securing the Internet of Things
Connected Consumer Products. Best Practice Guidelines
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & ECSO (European Cyber Security Organization)
Auto ISAC (Automotive Information Sharing and Analysis Center)
IIC (Industrial Internet Consortium)
IoT Security Foundation
NIST
OpenAI and others
ENISA
Cloud Security Alliance
Homeland Security
IoT Security Foundation
SANS Institute
IIC (Industrial Internet Consortium)
NIST & http://ecs-org.eu/documents/publications/5ad7268b92497.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
77 & ENISA Industry 4.0 & requirement & GP-TM-46 & Ensure security capabilities and interoperability between protocols when implementing different protocols for various devices within the same system. One of the example methods to achieve this is by using dedicated gateways that provide translation of protocols. A gateway can translate an insecure protocol into a modern, secure protocol before sending it further, thus reducing the attack surface. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Outages & Security Guidance for Early Adopters of the Internet of Things
Baseline Security Recommendations for IoT
Industrial Internet of Things Volume G4: Security Framework
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.14 IoT Security Guidelines for Network Operators
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns & Cloud Security Alliance
ENISA
IIC (Industrial Internet Consortium)
IEC
GSMA (Global System for Mobile Communications)
SANS Institute & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2017/10/CLP.14-v2.0.pdf
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
78 & ENISA Industry 4.0 & requirement & GP-PS-16 & Deploy a new device into the system only according to an established, accepted and communicated change management process. Do not allow for any changes unless designated approvals are received. Approved changes should be documented and the relevant documentation updated. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental) & NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
Industrial Internet of Things Volume G4: Security Framework
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Putting Industrial Cyber Security at the top of the CEO agenda
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & NIST
IIC (Industrial Internet Consortium)
Siemens
NIST
NIST
LNS
ISO
ISO
IEC
IIC (Industrial Internet Consortium)
NIST & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
79 & ENISA Industry 4.0 & requirement & GP-TM-58 & Harden IIoT solutions and include this in the change management policy. Ensure that all unused network ports, protocols and unnecessary functionalities of the devices are disabled and that test/debug features are locked. Hardening should include, where applicable, operation system, software, firmware and application. In addition, perform periodic checks of critical samples at least annually and in case of a major change to the system. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking
Physical attacks
Failures / Malfunctions & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks
IoT Security Maturity Model: Description and Intended Use & Siemens
OWASP (Open Web Application Security Project)
NIST
OpenAI and others
ENISA
Cloud Security Alliance
Symantec
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
NIST
IIC (Industrial Internet Consortium) & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
80 & ENISA Industry 4.0 & requirement & GP-PS-22 & To be informed on the potential attack types and sources and new vulnerabilities which are relevant to your company’s field of operation, consider incorporating threat intelligence process within the threat management approach. & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
GSMA CLP.14 IoT Security Guidelines for Network Operators
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & Symantec
GSMA (Global System for Mobile Communications)
NIST
Cloud Security Alliance
IoT Alliance Australia
ISO
NIST
Huawei
IEC
IIC (Industrial Internet Consortium) & https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://www.gsma.com/iot/wp-content/uploads/2017/10/CLP.14-v2.0.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
81 & ENISA Industry 4.0 & requirement & GP-OP-11 & Consider creation of OT Cybersecurity Operations Centre (SOC) consisting of specialists with clear roles, responsibilities and IT, OT and cybersecurity competences to support cybersecurity incidents. Divide them into specific lines of support with appropriate roles and responsibilities. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Incidents handling & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Industrial Internet of Things Volume G4: Security Framework
Putting Industrial Cyber Security at the top of the CEO agenda
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security & Symantec
IIC (Industrial Internet Consortium)
LNS
NIST
IEC
NIST & https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
82 & ENISA Industry 4.0 & requirement & GP-TM-45 & For IIoT solutions implement proven-in-use protocols (rather than recently introduced ones) with known security capabilities, based on standards and technical recommendations. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions
Outages & IoT Security Guidance
IoT Security Guidelines for Network Operators
Internet of Things (IoT) Security and Privacy Recommendations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Identity and Access Management for the Internet of Things - Summary Guidance
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
Security Guidance for Early Adopters of the Internet of Things
Connected Consumer Products. Best Practice Guidelines
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & OWASP (Open Web Application Security Project)
GSMA (Global System for Mobile Communications)
BITAG (Broadband Internet Technical Advisory Group)
NIST
ENISA
Cloud Security Alliance
IoT Alliance Australia
IIC (Industrial Internet Consortium)
Huawei
Cloud Security Alliance
IoT Security Foundation
NIST
IEC
NIST & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://www.gsma.com/iot/wp-content/uploads/2017/10/CLP.14-v2.0.pdf
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
83 & ENISA Industry 4.0 & requirement & GP-PS-02 & Address cybersecurity through embedded features of endpoints rather than only on the network level, if it is possible considering constraints such as limited computing power. Embed cybersecurity in automation systems by introducing fail-safe and fail-secure mechanisms from design. & \textit{NULL} & \textit{NULL} & I. Policies & Security by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Failures / Malfunctions
 & Security Guidance for Early Adopters of the Internet of Things
Industry 4.0: Secure by design
Automotive Cybersecurity Best Practices - Executive Summary
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
IIC Endpoint Security Best Practices
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
VDC
Auto ISAC (Automotive Information Sharing and Analysis Center)
OpenAI and others
IIC (Industrial Internet Consortium)
Symantec
IoT Alliance Australia
IIC (Industrial Internet Consortium)
Huawei
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
84 & ENISA Industry 4.0 & requirement & GP-TM-35 & Change default passwords and usernames during commissioning/first use. Use strong passwords aligned to internal password complexity policy and require setting of a new password after a defined period. Device manufacturers and cloud services providers should give these options to users. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks & IoT Security Guidance
Baseline Security Recommendations for IoT
Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & OWASP (Open Web Application Security Project)
ENISA
Cloud Security Alliance
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
NIST
ISO
IEC
NIST
SANS Institute
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
85 & ENISA Industry 4.0 & requirement & GP-PS-24 & Regarding the Risk Management process, adopt two different approaches at the same time & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
Vulnerability Management: Tools, Challenges and Best Practices
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Industry 4.0: Secure by design
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & IIC (Industrial Internet Consortium)
SANS Institute
Cloud Security Alliance
IoT Alliance Australia
VDC
IEC & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
86 & ENISA Industry 4.0 & requirement & GP-TM-51 & Collect security logs (i.e. change logs, fault logs, performance logs) to enable analysis of events. To the extent possible, event logs should include user IDs, system activities, dates, times and details of key events (e.g. log-on and log-off times), use of privileges, etc. & \textit{NULL} & \textit{NULL} & III. Technical practices & Monitoring and auditing & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Industrial Internet of Things Volume G4: Security Framework
Industry 4.0: Secure by design
IEC 62443-3-3:2013 System security requirements and security levels
An Abbreviated History of Automation \& Industrial Controls Systems and Cybersecurity
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
IIC Endpoint Security Best Practices
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Connected Consumer Products. Best Practice Guidelines
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & IEC
IIC (Industrial Internet Consortium)
VDC
IEC
SANS Institute
Siemens
IIC (Industrial Internet Consortium)
OWASP (Open Web Application Security Project)
NIST
ENISA
Cloud Security Alliance
IoT Security Foundation
NIST & https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://webstore.iec.ch/publication/7033
https://ics.sans.org/media/An-Abbreviated-History-of-Automation-and-ICS-Cybersecurity.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
87 & ENISA Industry 4.0 & requirement & GP-TM-16 & In business continuity and recovery plans, include Third Parties aspects. Appropriate Third Party management and control over its involvement is essential for ensuring company's continuity of operations. & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental)
Failures / Malfunctions & BSI-Standards 100-4 - Business Continuity Management
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST Advanced Manufacturing Series 300-1 Reference Architecture for Smart Manufacturing Part 1: Functional Models
Hippocratic Oath for Connected Medical Devices
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls & Federal Office for Information Security (BSI)
NIST
NIST
The Cavalry
NIST
ISO & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-4\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ams/NIST.AMS.300-1.pdf
https://www.iamthecavalry.org/wp-content/uploads/2016/01/I-Am-The-Cavalry-Hippocratic-Oath-for-Connected-Medical-Devices.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
88 & ENISA Industry 4.0 & requirement & GP-TM-20 & Use communication protocols that include the functionality to detect if all or part of a message is an unauthorised repeat of an earlier message. & \textit{NULL} & \textit{NULL} & III. Technical practices & Machine-to-Machine security & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & TR 0008 Security V2.0.0 - Security. Technical Report
NIST SP 800-52 r1: Guidelines for the Selection, Configuration, and Use of Transport Layer Security (TLS) Implementations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & oneM2M
NIST
NIST
IoT Alliance Australia
IIC (Industrial Internet Consortium)
NIST
ISO
IEC
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & http://www.onem2m.org/images/files/deliverables/Release2/TR-0008-Security-V2\_0\_0.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-52r1.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
89 & ENISA Industry 4.0 & requirement & GP-PS-10 & Separate data that can be used to identify an individual from other information and ensure its security (for storing and retrieving information, communication services, cryptography, etc.). Any personal data transferred within the IIoT environment shall be encrypted in the traffic. & \textit{NULL} & \textit{NULL} & I. Policies & Privacy by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Legal & Security Guidance for Early Adopters of the Internet of Things
ETSI TR 103 375 SmartM2M; IoT Standards landscape and future evolutions
Connected Consumer Products. Best Practice Guidelines
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
ETSI (European Telecommunications Standards Institute)
IoT Security Foundation
IoT Alliance Australia
IIC (Industrial Internet Consortium)
Huawei
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.etsi.org/deliver/etsi\_tr/103300\_103399/103375/01.01.01\_60/tr\_103375v010101p.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
90 & ENISA Industry 4.0 & requirement & GP-TM-55 & Implement a mechanism and supporting tools that allow for configuration management. This mechanism should enable tracking of changes and recreation of the state of the system from before the change. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
Industrial Internet of Things Volume G4: Security Framework
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-3-3:2013 System security requirements and security levels
ANSI/ISA-95 Part 1: Models and Terminology
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & Siemens
IIC (Industrial Internet Consortium)
NIST
NIST
ISO
NIST
IEC
ISA
IEC & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7033
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
91 & ENISA Industry 4.0 & requirement & GP-OP-04 & Conduct cybersecurity acceptance tests against technical specification during different validation activities or stages of the product lifecycle, e.g. FAT, SAT and penetration testing before go-live. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Endpoints lifecycle & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Outages
Disasters & Industrial Internet of Things Volume G4: Security Framework
Security Challenges on the Way Towards Smart Manufacturing
Best practices in cyber supply chain risk management. Smart Manufacturing The Future of Manufacturing and Value Chain Competitiveness
Avoiding the internet of insecure industrial things
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & IIC (Industrial Internet Consortium)
IoT Security Foundation
NIST
Elsevier
ISO
NIST
ISO
IEC
IEC & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://www.nist.gov/sites/default/files/documents/itl/csd/NIST\_USRP-SmartManu-Cyber-SCRM-Case-Study.pdf
https://www.sciencedirect.com/science/article/pii/S0267364917303217
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
92 & ENISA Industry 4.0 & requirement & GP-PS-07 & Define the scope of the data that will be processed by the device as well as the objective of this processing during the design phase. Ensure that only a minimal amount of personal data is collected by the device. Avoid collecting sensitive data. If you are a user of an IIoT system, do not provide any personal or sensitive information if it is not necessary. & \textit{NULL} & \textit{NULL} & I. Policies & Privacy by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Legal & Security Guidance for Early Adopters of the Internet of Things
Security Challenges on the Way Towards Smart Manufacturing
Industry 4.0: Secure by design
IoT Security Guidance
Identity and Access Management for the Internet of Things - Summary Guidance
Connected Consumer Products. Best Practice Guidelines
Putting Industrial Cyber Security at the top of the CEO agenda
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ANSI/ISA-95 Part 1: Models and Terminology
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
IoT Security Foundation
VDC
OWASP (Open Web Application Security Project)
Cloud Security Alliance
IoT Security Foundation
LNS
NIST
ISA
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
93 & ENISA Industry 4.0 & requirement & GP-OP-06 & To ensure security in a computerised ecosystem, adopt a holistic architectural-based approach and develop a risk-aligned security architecture based on business requirements. & \textit{NULL} & \textit{NULL} & II. Organizational practices & IT Security architecture & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Putting Industrial Cyber Security at the top of the CEO agenda
Strategic Principles for Securing the Internet of Things
Industrial Internet of Things Volume G4: Security Framework
Industry 4.0: Secure by design
IEC 62443-3-3:2013 System security requirements and security levels
ANSI/ISA-95 Part 1: Models and Terminology
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.11 IoT Security Guidelines Overview Document & LNS
Homeland Security
IIC (Industrial Internet Consortium)
VDC
IEC
ISA
Huawei
IEC
GSMA (Global System for Mobile Communications) & https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://webstore.iec.ch/publication/7033
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
94 & ENISA Industry 4.0 & requirement & GP-PS-12 & Ensure that your company has a consistent and up-to-date asset inventory. This inventory should include, among others, IP addresses, physical location, host, current firmware / OS version, used communication protocols, etc. The asset inventory should also include gathered known vulnerabilities related to particular assets. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking
Physical attacks
Failures / Malfunctions & NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
Security Guidance for Early Adopters of the Internet of Things
Identity and Access Management for the Internet of Things - Summary Guidance
Vulnerability Management: Tools, Challenges and Best Practices
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & NIST
Cloud Security Alliance
Cloud Security Alliance
SANS Institute
NIST
NIST
ISO
ISO
IEC
IEC
SANS Institute
NIST & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://webstore.iec.ch/publication/7030
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
95 & ENISA Industry 4.0 & requirement & GP-TM-03 & Define data exchange channels between IIoT devices and ensure that the system owner accepts them. Choose only secure channels whenever possible and implement whitelists. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking & Accompanying the Industrial Internet of Things Volume G1: Reference architecture
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
Mobile Top 10 2016
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & IIC (Industrial Internet Consortium)
IIC (Industrial Internet Consortium)
NIST
Huawei
NIST
IEC
SANS Institute
OWASP (Open Web Application Security Project)
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://webstore.iec.ch/publication/7030
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://www.owasp.org/index.php/Mobile\_Top\_10\_2016-Top\_10
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
96 & ENISA Industry 4.0 & requirement & GP-TM-59 & Create and apply a comprehensive backup plan, including provisions for periodic testing, tailored to different types of assets. Perform backups before updates and other important changes to the system. For some assets, backups should be made regularly with the frequency depending on the asset type. When making a backup, verify whether it will work properly (perform a test of the backup). To do so, you may check hash or use a dedicated application. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Outages
Disasters & NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & NIST
NIST
ISO
IEC
NIST
ISO
IEC & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iso.org/standard/54534.html
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
97 & ENISA Industry 4.0 & requirement & GP-TM-09 & In cloud-based application and centralised systems, avoid single points of failure. & \textit{NULL} & \textit{NULL} & III. Technical practices & Cloud security & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Outages & Security Guidance for Early Adopters of the Internet of Things
Industrial Internet of Things Volume G4: Security Framework
Future Proofing the connected world
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
Building the New Network Security Architecture for the Future & Cloud Security Alliance
IIC (Industrial Internet Consortium)
Cloud Security Alliance
GSMA (Global System for Mobile Communications)
SANS Institute & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/future-proofing-the-connected-world.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
98 & ENISA Industry 4.0 & requirement & GP-TM-10 & Locate critical systems and applications within the private or at least hybrid deployment models. If you consider utilisation of a public cloud, precede this decision with risk analysis. & \textit{NULL} & \textit{NULL} & III. Technical practices & Cloud security & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions & Industrial Internet of Things Volume G4: Security Framework
IoT trust framework 2.5
Building the New Network Security Architecture for the Future
NIST SP 800-146 Cloud Computing Synopsis and Recommendations
INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector & IIC (Industrial Internet Consortium)
Online Trust Alliance
SANS Institute
NIST
ECSO (European Cyber Security Organization) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://otalliance.org/system/files/files/initiative/documents/iot\_trust\_framework6-22.pdf
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-146.pdf
http://ecs-org.eu/documents/publications/5ad7268b92497.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
99 & ENISA Industry 4.0 & requirement & GP-OP-09 & Integrate compliance enforcement controls to the established Security Architecture and ensure that all products meet the requirements defined within it. & \textit{NULL} & \textit{NULL} & II. Organizational practices & IT Security architecture & \textit{NULL} & \textit{NULL} & Failures / Malfunctions
Unintentional damages (accidental)
Legal
Disasters & Strategic Principles for Securing the Internet of Things
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Industrial Internet of Things Volume G4: Security Framework
IoT Security Maturity Model: Description and Intended Use
ANSI/ISA-95 Part 1: Models and Terminology
Putting Industrial Cyber Security at the top of the CEO agenda
Accompanying the Industrial Internet of Things Volume G1: Reference architecture
Building the New Network Security Architecture for the Future & Homeland Security
IEC
IIC (Industrial Internet Consortium)
IIC (Industrial Internet Consortium)
ISA
LNS
IIC (Industrial Internet Consortium)
SANS Institute & https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
100 & ENISA Industry 4.0 & requirement & GP-TM-21 & Use positive/whitelist input validation to protect against cross site scripting and command injection, i.e. decode any encoded input and then validate the length, characters, and format on that data before accepting the input. & \textit{NULL} & \textit{NULL} & III. Technical practices & Machine-to-Machine security & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Internet of Things Security Guidelines v1.2
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems & Siemens
NIST
ENISA
IoT Alliance Australia
IEC
Huawei
IEC
GSMA (Global System for Mobile Communications) & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
101 & ENISA Industry 4.0 & requirement & GP-TM-40 & Within access control, include physical access to buildings, areas, rooms and cabinets locations (e.g. by means of walls, fences, electronic/mechanical locks and casings). Periodically revise access rights (especially to critical areas), limit physical access only to the required minimum and segregate it based on roles in the company. Ensure that the departure of an employee or change of a role within the company is followed by a prompt change/termination of physical access (e.g. physical access system can be connected to the HR system). & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Physical attacks & Identity and Access Management for the Internet of Things - Summary Guidance
Industrial Internet of Things Volume G4: Security Framework
NISTIR 8200: Interagency Report on Status of International Cybersecurity Standardization for the Internet of Things (IoT)
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Connected Consumer Products. Best Practice Guidelines
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Cloud Security Alliance
IIC (Industrial Internet Consortium)
NIST
NIST
NIST
Cloud Security Alliance
IoT Security Foundation
ISO
NIST
ISO
IEC
IIC (Industrial Internet Consortium)
NIST & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://csrc.nist.gov/publications/detail/nistir/8200/draft
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
102 & ENISA Industry 4.0 & requirement & GP-PS-09 & Conduct a Privacy Impact Analysis (PIA) for the data that will be processed by the device. It may be integrated with the overall risk management process. & \textit{NULL} & \textit{NULL} & I. Policies & Privacy by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Legal & Security Guidance for Early Adopters of the Internet of Things
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
Baseline Security Recommendations for IoT
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
World Economic Forum
ENISA
IoT Alliance Australia
IIC (Industrial Internet Consortium)
NIST
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
103 & ENISA Industry 4.0 & requirement & GP-TM-54 & Establish baseline security configurations tailored to different types of assets. Within these baselines include, among others, information about system components (e.g. required software that is installed with version numbers and patch information on operating systems, whitelists of applications, required ports, protocols, functions and set parameters), network topology, logical placement within the system architecture, etc. & \textit{NULL} & \textit{NULL} & III. Technical practices & Configuration Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & IIC (Industrial Internet Consortium)
NIST
NIST
NIST
IEC
Huawei
IEC
NIST & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
104 & ENISA Industry 4.0 & requirement & GP-OP-23 & To improve awareness, consider communicating with other companies on a sector level including the supply chain - communication with manufacturers, components providers, software providers, service providers and customers is recommended. Also, consider participation in international security infrastructures based on trust formed to enable discussion, cooperation and intelligence sharing across organisations. Examples of such infrastructures already exist and include Plattform Industrie 4.0, Industrial Internet Consortium, Cloud Security Alliance, etc. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Training and Awareness & \textit{NULL} & \textit{NULL} & Failures / Malfunctions & Identity and Access Management for the Internet of Things - Summary Guidance
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & Cloud Security Alliance
OpenAI and others
World Economic Forum
NIST
NIST
Cloud Security Alliance
ISO
NIST
ISO
IEC
IIC (Industrial Internet Consortium) & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
105 & ENISA Industry 4.0 & requirement & GP-OP-19 & Adopt a holistic approach to security training and awareness among employees – ensure that it includes employees on all levels of the organisation, covers new threats introduced to the manufacturing environment by Industry 4.0 new capabilities and is tailored to employees' roles and responsibilities as well as to the different levels of knowledge of the participants. Moreover, ensure that an additional training follows every change in employee responsibilities. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Training and Awareness & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Unintentional damages (accidental) & INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Industry 4.0: Security imperatives for IoT — converging networks, increasing risks.
Future Proofing the connected world
Industrie 4.0 Security Guidelines Recommendations for actions
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations & ECSO (European Cyber Security Organisation)
NIST
Shaun Bligh-Wall
Cloud Security Alliance
VDMA
Siemens
ISO
IEC
NIST & http://www.ecs-org.eu/documents/uploads/industry-40-and-ics-sector-report-032018.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.henrystewartpublications.com/sites/default/files/Bligh-Wall.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/future-proofing-the-connected-world.pdf
http://www.vdmashop.de/refs/Leitf\_I40\_Security\_En\_LR\_neu.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
106 & ENISA Industry 4.0 & requirement & GP-OP-24 & Strictly control access by Third Parties to a control or production layer, e.g. by physically plugging the RJ45 jack when the vendor has access or through timer systems. In addition, utilise dedicated registry accounts, multifactor authentication and encryption. Grant access to a control or production layer to Third Parties only on-demand, in a specified time window, for a specific purpose, and in a least privileged way. Record and supervise sessions and do not allow for idle sessions. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Third Party Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & INDUSTRY 4.0 AND ICS SECTOR REPORT Cyber security for the industry 4.0 and ICS sector
Automotive Cybersecurity Best Practices - Executive Summary
IoT Security Guidance
NISTIR 8200: Interagency Report on Status of International Cybersecurity Standardization for the Internet of Things (IoT)
Identity and Access Management for the Internet of Things - Summary Guidance
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & ECSO (European Cyber Security Organization)
Auto ISAC (Automotive Information Sharing and Analysis Center)
OWASP (Open Web Application Security Project)
NIST
Cloud Security Alliance
ISO
IIC (Industrial Internet Consortium)
NIST & http://ecs-org.eu/documents/publications/5ad7268b92497.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://csrc.nist.gov/publications/detail/nistir/8200/draft
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.iso.org/standard/54533.html
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
107 & ENISA Industry 4.0 & requirement & GP-TM-07 & Base your decisions regarding the choice of the type of cloud on a business and privacy impact assessment, i.e. a type of quantitative risk assessments, taking also into consideration laws and regulations applicable to cloud service provider’s country and points of presence. Risk based approach to assess the criticality is of great importance. & \textit{NULL} & \textit{NULL} & III. Technical practices & Cloud security & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental)
Failures / Malfunctions
Legal & Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
Future Proofing the connected world
IoT trust framework 2.5
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
Internet of Things Security Guidelines v1.2 & Cloud Security Alliance
Cloud Security Alliance
Cloud Security Alliance
Online Trust Alliance
GSMA (Global System for Mobile Communications)
IoT Alliance Australia & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/future-proofing-the-connected-world.pdf
https://otalliance.org/system/files/files/initiative/documents/iot\_trust\_framework6-22.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
108 & ENISA Industry 4.0 & requirement & GP-TM-34 & As an IIoT solutions vendor, implement multi-factor authentication capability (e.g. Apple Touch ID, security tokens). & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks & IoT Security Guidance
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Baseline Security Recommendations for IoT
Identity and Access Management for the Internet of Things - Summary Guidance
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & OWASP (Open Web Application Security Project)
OpenAI and others
ENISA
Cloud Security Alliance
IoT Security Foundation
IIC (Industrial Internet Consortium)
NIST
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
109 & ENISA Industry 4.0 & requirement & GP-TM-23 & Categorise data related to the OT system based on risk analysis. Take into account production, device and user information. Defined categories may include for example production schedule data, customer data, R\&D data, asset management data, defect and quality data, production line data, etc. For each category, assess the criticality of data and define required security measures that will ensure proper level of security. Recipes for instance are considered critical for manufacturing companies and shall be therefore protected with the most advanced measures, e.g. encryption. & \textit{NULL} & \textit{NULL} & III. Technical practices & Data protection & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse & Identity and Access Management for the Internet of Things - Summary Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & Cloud Security Alliance
NIST
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
ISO
ISO
IEC
IIC (Industrial Internet Consortium) & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
110 & ENISA Industry 4.0 & requirement & GP-TM-24 & Grant access to certain categories of data to Third Parties with least privilege and need-to-know principles in mind and document this access, i.e. ensure that Third Parties have access only to the necessary data and have minimal privileges, e.g. read only access to data that they should not be alter. & \textit{NULL} & \textit{NULL} & III. Technical practices & Data protection & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental) & Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Cloud Security Alliance
Cloud Security Alliance
IoT Alliance Australia
IIC (Industrial Internet Consortium)
NIST
ISO
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium)
NIST & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
111 & ENISA Industry 4.0 & requirement & GP-OP-07 & While defining security architecture, ensure that it comprises all relevant security aspects – from organisational to physical implementation issues. & \textit{NULL} & \textit{NULL} & II. Organizational practices & IT Security architecture & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Strategic Principles for Securing the Internet of Things
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
Industrial Internet of Things Volume G4: Security Framework
IoT Security Maturity Model: Description and Intended Use
ANSI/ISA-95 Part 1: Models and Terminology
Putting Industrial Cyber Security at the top of the CEO agenda
Industry 4.0: Secure by design & Homeland Security
Huawei
IEC
IEC
IIC (Industrial Internet Consortium)
IIC (Industrial Internet Consortium)
ISA
LNS
VDC & https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
112 & ENISA Industry 4.0 & requirement & GP-PS-04 & Perform risk and threat analysis involving cybersecurity experts from the very early stages of the design process of the device to find out which security features will be necessary. The analysis should include possible and tailored use cases that the device may encounter. It is recommended to develop threat modelling for the IIoT systems and attack trees to consider resilience to various attack scenarios. Cybersecurity experts should be involved in the process to provide insights on threats and risks that the control systems are facing based on the experience and knowledge of current threat and risk landscape. & \textit{NULL} & \textit{NULL} & I. Policies & Security by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Security Guidance for Early Adopters of the Internet of Things
Automotive Cybersecurity Best Practices - Executive Summary
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Internet of Things Security Guidelines v1.2
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security White Paper 2017
GSMA CLP.11 IoT Security Guidelines Overview Document
IoT Security Maturity Model: Description and Intended Use & Cloud Security Alliance
Auto ISAC (Automotive Information Sharing and Analysis Center)
NIST
IIC (Industrial Internet Consortium)
NIST
Symantec
IoT Alliance Australia
ISO
Huawei
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iso.org/standard/54533.html
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
113 & ENISA Industry 4.0 & requirement & GP-PS-15 & Consider secure administration of assets, e.g. utilise secure/encrypted methods for administration of IoT devices (e.g. HTTPS, SSH) and associated key management. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse & Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
IEC 62443-3-3:2013 System security requirements and security levels
Internet of Things (IoT) Security and Privacy Recommendations
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
NIST
IEC
BITAG (Broadband Internet Technical Advisory Group)
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium)
NIST & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://webstore.iec.ch/publication/7033
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
114 & ENISA Industry 4.0 & requirement & GP-PS-14 & Use a centralised asset inventory for the overall computerised environment inside a manufacturing plant. While implementing change to a system, update the inventory. Store the latest version of software after implementation and after every change. Periodic reviews, e.g. annually, are also recommended. It is also advisable to use security tools that enable configuration management and change detection. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Physical attacks
Unintentional damages (accidental) & Industrial Internet of Things Volume G4: Security Framework
Identity and Access Management for the Internet of Things - Summary Guidance
Vulnerability Management: Tools, Challenges and Best Practices
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & IIC (Industrial Internet Consortium)
Cloud Security Alliance
SANS Institute
Cloud Security Alliance
NIST
IEC & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
115 & ENISA Industry 4.0 & requirement & GP-TM-04 & Implement application whitelists, i.e. lists of applications that are allowed to run in the industrial control environment and mechanisms that prevent all other applications from running. Such lists shall be provided by vendor or defined in consultation with the vendor and reviewed at least annually and in case of implementation of a change to the system. On the whitelists, all unnecessary applications and applications with known vulnerabilities shall be avoided, as they contain backdoors to the system that can be used by attackers. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental)
Failures / Malfunctions
Outages & Identity and Access Management for the Internet of Things - Summary Guidance
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
Industrial Internet of Things Volume G4: Security Framework
Internet of Things Security Guidelines v1.2
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
An Internet of Things Reference Architecture & Cloud Security Alliance
IEC
IEC
IIC (Industrial Internet Consortium)
IoT Alliance Australia
NIST
NIST
Symantec & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.symantec.com/content/en/us/enterprise/white\_papers/iot-security-reference-architecture-wp-en.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
116 & ENISA Industry 4.0 & requirement & GP-TM-25 & For data of high confidentiality, implement encryption and key management so that the information can be read only by authorised users. In addition, use data loss prevention solutions. & \textit{NULL} & \textit{NULL} & III. Technical practices & Data protection & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Unintentional damages (accidental) & Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations & Symantec
NIST
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
ISO
IEC
Huawei
NIST & https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
117 & ENISA Industry 4.0 & requirement & GP-PS-23 & From an organisational perspective, monitor selected threats and determine their impact on systems by performing risk analysis. Control threats detected through the threat intelligence process. & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Automotive Cybersecurity Best Practices - Executive Summary
NIST SP 800 30r1 - Guide for Conducting Risk Assessments
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
GSMA CLP.11 IoT Security Guidelines Overview Document
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Security Guidance for Early Adopters of the Internet of Things
Security capabilities supporting safety of the Internet of things
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use & Auto ISAC (Automotive Information Sharing and Analysis Center)
NIST
Symantec
GSMA (Global System for Mobile Communications)
NIST
Cloud Security Alliance
International Telecommunications Union
IIC (Industrial Internet Consortium)
Huawei
NIST
IIC (Industrial Internet Consortium) & http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-30r1.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.itu.int/rec/T-REC-Y.4806/en
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
118 & ENISA Industry 4.0 & requirement & GP-OP-16 & Establish tight collaboration between the OT and IT department. Do not allow any individual responsible for IT security to implement any cybersecurity policies, including vulnerability management, on the OT side without the full knowledge and cooperation of the plant engineers. Ensure that IT and OT departments share their knowledge about systems operations as well as about threats. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Vulnerabilities Management & \textit{NULL} & \textit{NULL} & Unintentional damages (accidental) & Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Putting Industrial Cyber Security at the top of the CEO agenda
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
IoT Security Maturity Model: Description and Intended Use & Symantec
NIST
LNS
NIST
Huawei
SANS Institute
IIC (Industrial Internet Consortium) & https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
119 & ENISA Industry 4.0 & requirement & GP-TM-50 & Implement passive monitoring solution in the IT and OT environments to create industrial network traffic baseline and monitor anomalies and adherence to the baseline. & \textit{NULL} & \textit{NULL} & III. Technical practices & Monitoring and auditing & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & Security Guidance for Early Adopters of the Internet of Things
An Internet of Things Reference Architecture
BSI-Standards 100-1 - Information Security Management Systems (ISMS)
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Industrial Internet of Things Volume G4: Security Framework
Putting Industrial Cyber Security at the top of the CEO agenda
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Cloud Security Alliance
Symantec
Federal Office for Information Security (BSI)
Siemens
Symantec
IIC (Industrial Internet Consortium)
LNS
NIST
Huawei
NIST
IEC
SANS Institute
NIST & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.symantec.com/content/en/us/enterprise/white\_papers/iot-security-reference-architecture-wp-en.pdf
https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-1\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://webstore.iec.ch/publication/7030
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
120 & ENISA Industry 4.0 & requirement & GP-OP-12 & Establish a process for incidents handling that consists of identification of affected assets, identification and classification of vulnerabilities, escalation and notification. Make a revision of the process at least annually and as soon as possible in case of a major change, e.g. change in organisational hierarchy, contracts, etc. Update the process with lessons learned from analysing and resolving security incidents. Test the process at least annually and consider different possible incidents. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Incidents handling & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
Identity and Access Management for the Internet of Things - Summary Guidance
Automotive Cybersecurity Best Practices - Executive Summary
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Security Guidance for Early Adopters of the Internet of Things
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
Cloud Security Alliance
Auto ISAC (Automotive Information Sharing and Analysis Center)
NIST
NIST
ENISA
Cloud Security Alliance
Symantec
NIST
ISO
IEC
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
121 & ENISA Industry 4.0 & requirement & GP-PS-05 & In each design document include a chapter addressing security of all information and control systems in industrial environment. & \textit{NULL} & \textit{NULL} & I. Policies & Security by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Security Guidance for Early Adopters of the Internet of Things
Automotive Cybersecurity Best Practices - Executive Summary
ETSI GR QSC 004 V1.1.1 (2017-03) Quantum Safe Cryptography; Quantum-Safe threat assessment
Connected Consumer Products. Best Practice Guidelines
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ANSI/ISA-95 Part 1: Models and Terminology
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
Auto ISAC (Automotive Information Sharing and Analysis Center)
ETSI (European Telecommunications Standards Institute)
IoT Security Foundation
NIST
ISA
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
http://www.etsi.org/deliver/etsi\_gr/QSC/001\_099/004/01.01.01\_60/gr\_QSC004v010101p.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.isa.org/store/ansi/isa-950001-2010-iec-62264-1-mod-enterprise-control-system-integration-part-1-models-and-terminology/116636 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
122 & ENISA Industry 4.0 & requirement & GP-TM-36 & Apply the least privilege principle when setting user privileges. Ensure that in an environment with multiple users, roles are properly segregated and approved by the right person. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental) & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
Industrial Internet of Things Volume G4: Security Framework
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & Siemens
IIC (Industrial Internet Consortium)
OWASP (Open Web Application Security Project)
NIST
ENISA
NIST
ISO
IEC
Huawei
IEC
NIST
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
123 & ENISA Industry 4.0 & requirement & GP-PS-18 & Adopt an approach to risk management dedicated to Industry 4.0 and Smart Manufacturing. The approach to risk management can be qualitative or quantitative. Consider new parameters, threats and attack scenarios and cover all interdependencies between cyber-physical scenarios, cyber-physical environmental and safety during the assessment phase. & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
NIST.SP 1500-202 - Framework for Cyber-Physical Systems: Volume 2, Working Group Reports
Vulnerability Management: Tools, Challenges and Best Practices
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
NIST
SANS Institute
NIST
Symantec
NIST
Cloud Security Alliance
NIST
Huawei
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.1500-202.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
124 & ENISA Industry 4.0 & requirement & GP-OP-15 & While eliminating security gaps, begin from the most critical vulnerabilities taking into account the criticality of assets and systems. This process may be supported by asset inventory, if the inventory contains data related to assets and systems criticality. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Vulnerabilities management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions
Outages & Security Guidance for Early Adopters of the Internet of Things
Strategic Principles for Securing the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Vulnerability Management: Tools, Challenges and Best Practices & Cloud Security Alliance
Homeland Security
NIST
NIST
NIST
OpenAI and others
SANS Institute & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
125 & ENISA Industry 4.0 & requirement & GP-OP-20 & Provide all newly hired employees with cybersecurity training before starting the job. Provide all users of IIoT solutions with basic security awareness and training materials before they receive authorisation to access the system. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Training and Awareness & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Unintentional damages (accidental) & NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & NIST
World Economic Forum
NIST
NIST
ISO
IEC & https://nvlpubs.nist.gov/nistpubs/specialpublications/nist.sp.800-82r2.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
126 & ENISA Industry 4.0 & requirement & GP-OP-18 & Conduct penetration tests of new IIoT solutions in a controlled environment (e.g. in a lab, testing environment) or before / during commissioning phase (e.g. during FAT or SAT phase). In addition, conduct penetration tests regularly, e.g. once every 2 or 3 years, and after an important update of the system with acceptance of the system owner. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Vulnerabilities management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions & Vulnerability Management: Tools, Challenges and Best Practices
Internet of Things (IoT) Security Best Practices
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Putting Industrial Cyber Security at the top of the CEO agenda
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use & SANS Institute
IEEE
NIST
NIST
OpenAI and others
Cloud Security Alliance
IoT Alliance Australia
LNS
Huawei
IEC
NIST
IIC (Industrial Internet Consortium) & https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://internetinitiative.ieee.org/images/files/resources/white\_papers/internet\_of\_things\_feb2017.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
127 & ENISA Industry 4.0 & requirement & GP-TM-11 & To mitigate the risk related to cloud attacks, adopt a zero-knowledge security approach. It means that providers of services should store and manage data without access to encryption keys. & \textit{NULL} & \textit{NULL} & III. Technical practices & Cloud Security & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Identity and Access Management for the Internet of Things - Summary Guidance
Security Guidance for Early Adopters of the Internet of Things
Industrial Internet of Things Volume G4: Security Framework
Future Proofing the connected world
IoT trust framework 2.5
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems & Cloud Security Alliance
Cloud Security Alliance
IIC (Industrial Internet Consortium)
Cloud Security Alliance
Online Trust Alliance
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/future-proofing-the-connected-world.pdf
https://otalliance.org/system/files/files/initiative/documents/iot\_trust\_framework6-22.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
128 & ENISA Industry 4.0 & requirement & GP-TM-43 & Follow micro segmentation approach that is based on building within the same network (e.g. IT or OT) small islands of components that communicate only inside these islands. Control traffic between different segments using a firewall. While segmenting the network, use the principles of least privilege and need-to-know. This means that only the necessary system-to-system communication using necessary protocols on necessary ports should be allowed and the rest should be disabled. In case of an infection, isolated micro-segments prevent it from spreading further onto the network. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
Putting Industrial Cyber Security at the top of the CEO agenda
IEC 62443-3-3:2013 System security requirements and security levels
Building the New Network Security Architecture for the Future
IEC 62443-1-1:2009 Terminology, concepts and models
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & NIST
IoT Alliance Australia
IIC (Industrial Internet Consortium)
LNS
IEC
SANS Institute
IEC
IEC & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://webstore.iec.ch/publication/7033
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255
https://webstore.iec.ch/publication/7029
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
129 & ENISA Industry 4.0 & requirement & GP-TM-14 & Develop written procedures on how to return to the normal – well-defined – state of operation. Before establishing these procedures, perform threat and risk assessment and tailor the procedures to the assessment's results. Within the procedures, define roles and responsibilities for particular required actions. Distribute copies of the incident response plan to active incident response personnel. & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Vulnerability Management: Tools, Challenges and Best Practices
Identity and Access Management for the Internet of Things - Summary Guidance
Automotive Cybersecurity Best Practices - Executive Summary
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & SANS Institute
Cloud Security Alliance
Auto ISAC (Automotive Information Sharing and Analysis Center)
NIST
NIST
NIST
ISO
IEC & https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
130 & ENISA Industry 4.0 & requirement & GP-PS-01 & Treat IoT cybersecurity as a cycle - not as an end-to-end process. Take into consideration cybersecurity aspects in any activity of the development of the solution from the very beginning. Adopt security by design approach both from the devices as well as from the infrastructure perspective. & \textit{NULL} & \textit{NULL} & I. Policies & Security by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Security Guidance for Early Adopters of the Internet of Things
Industry 4.0: Secure by design
Automotive Cybersecurity Best Practices - Executive Summary
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
The Malicious Use of Artificial Intelligence: Forecasting, Prevention, and Mitigation
Baseline Security Recommendations for IoT
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
GSMA CLP.11 IoT Security Guidelines Overview Document & Cloud Security Alliance
VDC
Auto ISAC (Automotive Information Sharing and Analysis Center)
NIST
IIC (Industrial Internet Consortium)
OWASP (Open Web Application Security Project)
NIST
OpenAI and others
ENISA
IEC
GSMA (Global System for Mobile Communications) & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.eff.org/files/2018/02/20/malicious\_ai\_report\_final.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
https://webstore.iec.ch/publication/7030
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
131 & ENISA Industry 4.0 & requirement & GP-PS-11 & Utilise tools supporting asset management (i.e. automatic asset discovery). Asset management systems should be solid and robust. & \textit{NULL} & \textit{NULL} & I. Policies & Asset Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Failures / Malfunctions & NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
Industrial Internet of Things Volume G4: Security Framework
Security Guidance for Early Adopters of the Internet of Things
Identity and Access Management for the Internet of Things - Summary Guidance
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
IEC 62443-3-3:2013 System security requirements and security levels & NIST
IIC (Industrial Internet Consortium)
Cloud Security Alliance
Cloud Security Alliance
World Economic Forum
NIST
IEC & https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://webstore.iec.ch/publication/7033 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
132 & ENISA Industry 4.0 & requirement & GP-TM-42 & Segment industrial plants networks based on a pre-defined zoning model (e.g. into Office Layer, Manufacturing Layer and Control Layer according to the Purdue Model). & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Baseline Security Recommendations for IoT
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework
Putting Industrial Cyber Security at the top of the CEO agenda
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
IEC 62443-3-3:2013 System security requirements and security levels
IoT Security White Paper 2017
Building the New Network Security Architecture for the Future
IEC 62443-1-1:2009 Terminology, concepts and models
The 2018 SANS Industrial IoT Security Survey: Shaping IIoT Security Concerns
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Siemens
NIST
ENISA
IoT Alliance Australia
IIC (Industrial Internet Consortium)
LNS
ISO
IEC
Huawei
SANS Institute
IEC
SANS Institute
NIST & https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.honeywellprocess.com/en-US/online\_campaigns/lns-cyber-report/Pages/Honeywell-LNS-Study\_PuttingIndustrialCyberSecurityattheTopCEOAgenda.pdf
https://www.iso.org/standard/54534.html
https://webstore.iec.ch/publication/7033
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.sans.org/reading-room/whitepapers/cloud/building-network-security-architecture-future-38255
https://webstore.iec.ch/publication/7029
https://www.sans.org/reading-room/whitepapers/analyst/2018-industrial-iot-security-survey-shaping-iiot-security-concerns-38505
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
133 & ENISA Industry 4.0 & requirement & GP-TM-53 & Monitor the availability of the IIoT devices in real time, where technically feasible. & \textit{NULL} & \textit{NULL} & III. Technical practices & Monitoring and auditing & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Disasters & IEC 62443-3-3:2013 System security requirements and security levels
Embedded HW Security for IoT Applications
ETSI GR QSC 004 V1.1.1 (2017-03) Quantum Safe Cryptography; Quantum-Safe threat assessment
NISTIR 8200: Interagency Report on Status of International Cybersecurity Standardization for the Internet of Things (IoT)
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Internet of Things Security Guidelines v1.2
Industrial Internet of Things Volume G4: Security Framework & IEC
Smart Card Alliance
ETSI (European Telecommunications Standards Institute)
NIST
NIST
IoT Alliance Australia
IIC (Industrial Internet Consortium) & https://webstore.iec.ch/publication/7033
https://www.securetechalliance.org/downloads/Embedded-HW-Security-for-IoT-WP-FINAL-December-2016.pdf
http://www.etsi.org/deliver/etsi\_gr/QSC/001\_099/004/01.01.01\_60/gr\_QSC004v010101p.pdf
https://csrc.nist.gov/publications/detail/nistir/8200/draft
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
134 & ENISA Industry 4.0 & requirement & GP-TM-19 & Establish a security association with proven and secure cryptographic algorithms between the communicating entities to provide mutual authentication, integrity and confidentiality. & \textit{NULL} & \textit{NULL} & III. Technical practices & Machine-to-Machine security & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking & TR 0008 Security V2.0.0 - Security. Technical Report
An Internet of Things Reference Architecture
NIST SP 800-52 r1: Guidelines for the Selection, Configuration, and Use of Transport Layer Security (TLS) Implementations
IoT Security White Paper 2017
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use & oneM2M
Symantec
NIST
Huawei
NIST
Cloud Security Alliance
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
NIST
IIC (Industrial Internet Consortium) & http://www.onem2m.org/images/files/deliverables/Release2/TR-0008-Security-V2\_0\_0.pdf
https://www.symantec.com/content/en/us/enterprise/white\_papers/iot-security-reference-architecture-wp-en.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-52r1.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
135 & ENISA Industry 4.0 & requirement & GP-OP-13 & Detect and investigate promptly every unusual security related event. Require employees, contractors and external companies with access to the IT/OT environment to notify and report about any observed or suspected security weaknesses and anomalies. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Incidents handling & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages & Industrial Internet of Things Volume G4: Security Framework
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Security Guidance for Early Adopters of the Internet of Things
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
IEC 62443-3-3:2013 System security requirements and security levels
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
Symantec
NIST
Cloud Security Alliance
IEC
IEC
NIST
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://webstore.iec.ch/publication/7030
https://webstore.iec.ch/publication/7033
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
136 & ENISA Industry 4.0 & requirement & GP-TM-01 & Verify the integrity of the software before starting to run it. Verify the root of trust and secure boot mechanisms. Ensure that the software comes from a reliable source (signed by the vendor) and that it is obtained in a secure manner, e.g. downloaded via an encrypted connection. & \textit{NULL} & \textit{NULL} & III. Technical practices & Trust and Integrity Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks & Accompanying the Industrial Internet of Things Volume G1: Reference architecture
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
Baseline Security Recommendations for IoT
Internet of Things Security Guidelines v1.2
Connected Consumer Products. Best Practice Guidelines
Industrial Internet of Things Volume G4: Security Framework
Industry 4.0: Secure by design
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security White Paper 2017
IEC 62443-3-3:2013 System security requirements and security levels
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & IIC (Industrial Internet Consortium)
NIST
IIC (Industrial Internet Consortium)
ENISA
IoT Alliance Australia
IoT Security Foundation
IIC (Industrial Internet Consortium)
VDC
NIST
Huawei
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.iiconsortium.org/IIC\_PUB\_G1\_V1.80\_2017-01-31.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.enisa.europa.eu/publications/baseline-security-recommendations-for-iot
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7033
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
137 & ENISA Industry 4.0 & requirement & GP-OP-14 & Define a comprehensive vulnerability management process within the organisation that covers utilisation of automatic and manual tools, e.g. passive vulnerability scanners, resulting from risk analysis. In case of active scanners implementation, precede it with a testing phase and require acceptance by the system owner. Have in mind that active scanners in the OT environment may cause adverse effects to the system and disrupt the production process, especially if legacy equipment is used. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Vulnerabilities management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions & Industrial Internet of Things Volume G4: Security Framework
Automotive Cybersecurity Best Practices - Executive Summary
Vulnerability Management: Tools, Challenges and Best Practices
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IoT Security Maturity Model: Description and Intended Use
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & IIC (Industrial Internet Consortium)
Auto ISAC (Automotive Information Sharing and Analysis Center)
SANS Institute
NIST
ISO
ISO
IEC
NIST
IIC (Industrial Internet Consortium)
NIST & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://www.sans.org/reading-room/whitepapers/threats/vulnerability-management-tools-challenges-practices-1267
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
138 & ENISA Industry 4.0 & requirement & GP-TM-08 & Include security and availability aspects in agreements with cloud security providers. Responsibilities for cloud security aspects shall be clearly defined and allocated to particular parties or persons. Availability of service shall be measurable and defined through specified parameters. & \textit{NULL} & \textit{NULL} & III. Technical practices & Cloud security & \textit{NULL} & \textit{NULL} & Eavesdropping / Interception / Hijacking
Outages
Legal & BSI-Standards 100-4 - Business Continuity Management
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
Industrial Internet of Things Volume G4: Security Framework
IoT trust framework 2.5 & Federal Office for Information Security (BSI)
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium)
Online Trust Alliance & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-1\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://otalliance.org/system/files/files/initiative/documents/iot\_trust\_framework6-22.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
139 & ENISA Industry 4.0 & requirement & GP-TM-27 & Verify endpoints' software/firmware authenticity and integrity and ensure tight control over the update. Signing code updates (to be able to authenticate the code before it is loaded) and maintaining the authenticity is advisable. & \textit{NULL} & \textit{NULL} & III. Technical practices & Software/Firmware updates & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Failures / Malfunctions & Strategic Principles for Securing the Internet of Things
Connected Consumer Products. Best Practice Guidelines
Hippocratic Oath for Connected Medical Devices
Industrial Security: Applying IoT Security Controls on the Industrial Plant Floor
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
IIC Endpoint Security Best Practices
IoT Security Guidance
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & Homeland Security
IoT Security Foundation
The Cavalry
Siemens
NIST
IIC (Industrial Internet Consortium)
OWASP (Open Web Application Security Project)
NIST
Cloud Security Alliance
IoT Alliance Australia
ISO
GSMA (Global System for Mobile Communications) & https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://iotsecurityfoundation.org/wp-content/uploads/2016/12/Connected-Consumer-Products.pdf
https://www.iamthecavalry.org/wp-content/uploads/2016/01/I-Am-The-Cavalry-Hippocratic-Oath-for-Connected-Medical-Devices.pdf
https://www.industry.usa.siemens.com/automation/us/en/formsdocs/Documents/2016\%20MIA-\%2023\%20Industrial\%20Security\%20Applying\%20IoT\%20Security\%20Controls\%20on\%20the\%20Industrial\%20Plant\%20Floor.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/Endpoint\_Security\_Best\_Practices\_Final\_Mar\_2018.pdf
https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://www.iso.org/standard/54533.html
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
140 & ENISA Industry 4.0 & requirement & GP-PS-19 & For critical infrastructures in manufacturing environments, establish a number of risk management areas completely aligned with the corporate, safety, environmental, etc. sides. Assess and characterise threats, vulnerabilities and protection measures against those risk management areas. Based on that, in case of OT and Critical Infrastructures, build a specific impact-driven risk management approach. & \textit{NULL} & \textit{NULL} & I. Policies & Risk and Threat Management & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 30r1 - Guide for Conducting Risk Assessments
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Strategic Principles for Securing the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security Maturity Model: Description and Intended Use & IIC (Industrial Internet Consortium)
NIST
NIST
NIST
Homeland Security
NIST
ISO
IIC (Industrial Internet Consortium) & https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-30r1.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://www.dhs.gov/sites/default/files/publications/Strategic\_Principles\_for\_Securing\_the\_Internet\_of\_Things-2016-1115-FINAL....pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.iiconsortium.org/pdf/SMM\_Description\_and\_Intended\_Use\_2018-04-09.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
141 & ENISA Industry 4.0 & requirement & GP-TM-49 & Ensure the proper and effective use of cryptography to protect the confidentiality, authenticity and/or integrity of data and information (including control messages), in transit and in rest. Ensure the proper selection of standard and strong encryption algorithms and strong keys and disable insecure protocols. Verify the robustness of the implementation. & \textit{NULL} & \textit{NULL} & III. Technical practices & Networks, protocols and encryption & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking & Exploring IoT Security Volume 2
Internet of Things (IoT) Security and Privacy Recommendations
Future Proofing the connected world
AIOTI Digitisation of Industry Policy Recommendations
Internet Of Trust Security And Privacy In The Connected World
Protection Profile for the Gateway of a Smart Metering System (Smart Meter Gateway PP), Certification-ID: BSI-CC-PP-0073
GSMA CLP.11 IoT Security Guidelines Overview Document
Industrial Internet of Things Volume G4: Security Framework
Hardware Security for Smart Grid End Point Devices
Unleashing the potential of the Internet of Things
Best Current Practices for Securing Internet of Things (IoT) Devices
IETF RFC 7452 Architectural Considerations in Smart Object Networking
State-of-the-Art and Challenges for the Internet of Things Security
IOT-A (Internet of Things Architecture)
Performing a Security Risk Assessment
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements \#A10. Cryptography
ISO/IEC 27031:2011 Information technology -- Security techniques -- Guidelines for information and communication technology readiness for business continuity 7.4.3
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks
Framework for Improving Critical Infrastructure Cybersecurity V1.1
NIST SP 800 30r1 - Guide for Conducting Risk Assessments
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations - SC-13 Cryptographic Protection
Standards for M2M and the Internet of Things
Guide to Cryptography
Call it the Internet of Connected Things: The IoT Security Conundrum
Internet Security Threat Report (ISTR) Volume 22
Guidance for Securing IoT Using TCG Technology Reference Document & AT\&T Cybersecurity Insights
BITAG (Broadband Internet Technical Advisory Group)
Cloud Security Alliance
EC Alliance for Internet of Things Innovation (AIOTI)
EuroSMART (the voice of the Smart Security Industry)
Federal Office for Information Security (BSI)
GSMA (Global System for Mobile Communications)
IIC (Industrial Internet Consortium)
Infineon
International Telecommunications Union
Internet Engineering Task Force (IETF)
Internet Engineering Task Force (IETF)
Internet Research Task force (IRTF)
IOT-A (Internet of Things Architecture)
ISACA
ISO
ISO
NIST
NIST
NIST
NIST
oneM2M
OWASP (Open Web Application Security Project)
Software Assurance Forum for Excellence in Code (SAFECode) - NPO
Symantec
Trusted Computing Group (TCG) & https://www.business.att.com/cybersecurity/docs/exploringiotsecurity.pdf
https://www.bitag.org/documents/BITAG\_Report\_-\_Internet\_of\_Things\_(IoT)\_Security\_and\_Privacy\_Recommendations.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/future-proofing-the-connected-world.pdf
https://aioti-space.org/wp-content/uploads/2017/03/AIOTI-Digitisation-of-Ind-policy-doc-Nov-2016.pdf
http://www.eurosmart.com/news-publications/99-policy-papers/245-eurosmart-internet-of-trust-security-and-privacy-in-the-connected-world.html
https://www.commoncriteriaportal.org/files/ppfiles/pp0073b\_pdf.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.11-v1.1.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.nrel.gov/esif/assets/pdfs/hardware\_security\_smart\_grid.pdf
https://www.itu.int/en/publications/Documents/tsb/2016-InternetOfThings/index.html
https://www.ietf.org/proceedings/56/
https://tools.ietf.org/html/rfc7452
https://tools.ietf.org/pdf/draft-irtf-t2trg-iot-seccons-04.pdf
http://cordis.europa.eu/project/rcn/95713\_en.html
https://www.isaca.org/journal/archives/2010/volume-1/pages/performing-a-security-risk-assessment1.aspx
https://www.iso.org/standard/54534.html
https://www.iso.org/standard/44374.html
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf
https://nvlpubs.nist.gov/nistpubs/CSWP/NIST.CSWP.04162018.pdf
https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-30r1.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
http://www.onem2m.org/images/files/deliverables/Release2/TR-0008-Security-V2\_0\_0.pdf
https://www.owasp.org/index.php/Guide\_to\_Cryptography
http://www.safecode.org/call-it-the-internet-of-connected-things-the-iot-security-conundrum/
https://www.symantec.com/security-center/threat-report
https://resource.elq.symantec.com/LP=3980?cid=70138000001BjppAAC\&mc=202671\&ot=wp\&tt=sw\&inid=symc\_threat-report\_regular\_to\_leadgen\_form\_LP-3980\_ISTR22-report-main
https://trustedcomputinggroup.org/guidance-securing-iot-using-tcg-technology-reference-document/ & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
142 & ENISA Industry 4.0 & requirement & GP-TM-17 & Define important parameters for business continuity of your company, such as the recovery time objective (RTO), recovery point objective (RPO), maximum tolerable outage (MTO) and minimum business continuity objective (MBCO). & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & BSI-Standards 100-4 - Business Continuity Management
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST Advanced Manufacturing Series 300-1 Reference Architecture for Smart Manufacturing Part 1: Functional Models
Critical Security Controls
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & Federal Office for Information Security (BSI)
NIST
NIST
Center for Internet Security (CIS)
NIST
NIST
IEC & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-4\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ams/NIST.AMS.300-1.pdf
https://www.cisecurity.org/wp-content/uploads/2017/03/Poster\_Winter2016\_CSCs.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
143 & ENISA Industry 4.0 & requirement & GP-TM-38 & Implement in the device and/or use an account lockout functionality that activates after the number of failed login attempts exceeds the value of a set parameter. This also applies to cloud and mobile interfaces. & \textit{NULL} & \textit{NULL} & III. Technical practices & Access Control & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse & IoT Security Guidance
Security Guidance for Early Adopters of the Internet of Things
Internet of Things Security Guidelines v1.2
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-3-3:2013 System security requirements and security levels
GSMA CLP.12 IoT Security Guidelines for IoT Service Ecosystems
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems & OWASP (Open Web Application Security Project)
Cloud Security Alliance
IoT Alliance Australia
NIST
IEC
GSMA (Global System for Mobile Communications)
GSMA (Global System for Mobile Communications) & https://www.owasp.org/index.php/IoT\_Security\_Guidance
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
http://www.iot.org.au/wp/wp-content/uploads/2016/12/IoTAA-Security-Guideline-V1.2.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7033
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.12-v1.0.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
144 & ENISA Industry 4.0 & requirement & GP-PS-03 & Equip, as deemed appropriate after a security and safety assessment, even the most basic connected devices of very limited processing capabilities (e.g. actuators, converters) with identification and authentication features and ensure compatibility with IAM class solutions. & \textit{NULL} & \textit{NULL} & I. Policies & Security by design & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Physical attacks
Unintentional damages (accidental) & Security Guidance for Early Adopters of the Internet of Things
Industry 4.0: Secure by design
An Internet of Things Reference Architecture
Automotive Cybersecurity Best Practices - Executive Summary
Identity and Access Management for the Internet of Things - Summary Guidance
Industrial Internet of Things Volume G4: Security Framework
IoT Security White Paper 2017
GSMA CLP.13 IoT Security Guidelines for Endpoint Ecosystems
Draft NISTIR 8228: Considerations for Managing Internet of Things (IoT) Cybersecurity and Privacy Risks & Cloud Security Alliance
VDC
Symantec
Auto ISAC (Automotive Information Sharing and Analysis Center)
Cloud Security Alliance
IIC (Industrial Internet Consortium)
Huawei
GSMA (Global System for Mobile Communications)
NIST & https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://cdn2.hubspot.net/hubfs/582328/whitepapers/VDC\%20-\%20Industry\%204.0\%20Secure\%20by\%20Design\%20-\%20for\%20GrammaTech.pdf?t=1519834251604
https://www.symantec.com/content/en/us/enterprise/white\_papers/iot-security-reference-architecture-wp-en.pdf
http://www.sovereign-plc.co.uk/sites/default/files/Auto\%20ISAC\%20Cyber\%20Security\%20Best\%20Practices\%20Executive\%20Summary.pdf
https://downloads.cloudsecurityalliance.org/assets/research/internet-of-things/identity-and-access-management-for-the-iot.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://www.gsma.com/iot/wp-content/uploads/2016/02/CLP.13-v1.0.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2018/NIST.IR.8228-draft.pdf & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
145 & ENISA Industry 4.0 & requirement & GP-OP-21 & Ensure that security trainings are continuous and regular. Update the training programme after new important threats disclosure and adjust them according to the lessons learned from ongoing incident handling and recovery activities. & \textit{NULL} & \textit{NULL} & II. Organizational practices & Training and Awareness & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Unintentional damages (accidental) & Security Challenges on the Way Towards Smart Manufacturing
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Industrial Internet of Things: Unleashing the Potential of Connected Products and Services
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
Security Guidance for Early Adopters of the Internet of Things
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & IoT Security Foundation
NIST
World Economic Forum
NIST
Cloud Security Alliance
NIST
ISO
IEC & https://www.iotsecurityfoundation.org/security-challenges-on-the-way-towards-smart-manufacturing/
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
http://www3.weforum.org/docs/WEFUSA\_IndustrialInternet\_Report2015.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
146 & ENISA Industry 4.0 & requirement & GP-TM-13 & Define critical business and technological processes and determine to what extent they influence business continuity. & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & BSI-Standards 100-4 - Business Continuity Management
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST Advanced Manufacturing Series 300-1 Reference Architecture for Smart Manufacturing Part 1: Functional Models
Recommended Practice: Improving Industrial Control System Cybersecurity with Defense-in-Depth Strategies
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Security Guidance for Early Adopters of the Internet of Things
Smarter Security for Manufacturing in The Industry 4.0 Era: Industry 4.0 Cyber Resilience for the Manufacturing of the Future
Industrial Internet of Things Volume G4: Security Framework
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
IEC 62443-3-3:2013 System security requirements and security levels & Federal Office for Information Security (BSI)
NIST
NIST
Homeland Security
NIST
Cloud Security Alliance
Symantec
IIC (Industrial Internet Consortium)
NIST
IEC & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-4\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ams/NIST.AMS.300-1.pdf
https://ics-cert.us-cert.gov/sites/default/files/recommended\_practices/NCCIC\_ICS-CERT\_Defense\_in\_Depth\_2016\_S508C.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://downloads.cloudsecurityalliance.org/whitepapers/Security\_Guidance\_for\_Early\_Adopters\_of\_the\_Internet\_of\_Things.pdf
https://www.symantec.com/content/dam/symantec/docs/solution-briefs/industry-4.0-en.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://webstore.iec.ch/publication/7033 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
147 & ENISA Industry 4.0 & requirement & GP-TM-15 & Consider contingency planning preceded by a risk analysis. Define contingency plans and test them executing controlled exercises. Regularly review the plan (at least annually and in case of a major change) and adjust it appropriately. While preparing a contingency plan, consider both major disasters and smaller scale events caused by cyber incidents, which may disrupt normal operation of the company. Define responsible persons for every stage of the plan and establish a reporting process. Keep in mind that the plan needs to be simple and ensure employees' awareness through adequate training. & \textit{NULL} & \textit{NULL} & III. Technical practices & Business continuity and recovery & \textit{NULL} & \textit{NULL} & Nefarious Activity / Abuse
Eavesdropping / Interception / Hijacking
Physical attacks
Unintentional damages (accidental)
Failures / Malfunctions
Outages
Legal
Disasters & BSI-Standards 100-4 - Business Continuity Management
NIST SP 800 82r2: Guide to Industrial Control Systems (ICS) Security
NIST Advanced Manufacturing Series 300-1 Reference Architecture for Smart Manufacturing Part 1: Functional Models
ETSI GR QSC 004 V1.1.1 (2017-03) Quantum Safe Cryptography; Quantum-Safe threat assessment
NISTIR 8183: Cybersecurity Framework Manufacturing Profile
Industrial Internet of Things Volume G4: Security Framework
ISO/IEC 27001:2013 Information technology -- Security techniques -- Information security management systems -- Requirements
NIST SP 800 53r4: Security and Privacy Controls for Federal Information Systems and Organizations
ISO/IEC 27002:2013 Information technology -- Security techniques -- Code of practice for information security controls
IoT Security White Paper 2017
IEC 62443-2-1:2010 Establishing an industrial automation and control system security program & Federal Office for Information Security (BSI)
NIST
NIST
ETSI (European Telecommunications Standards Institute)
NIST
IIC (Industrial Internet Consortium)
ISO
NIST
ISO
Huawei
IEC & https://www.bsi.bund.de/SharedDocs/Downloads/EN/BSI/Publications/BSIStandards/standard\_100-4\_e\_pdf.pdf?\_\_blob=publicationFile\&v=1
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-82r2.pdf
https://nvlpubs.nist.gov/nistpubs/ams/NIST.AMS.300-1.pdf
http://www.etsi.org/deliver/etsi\_gr/QSC/001\_099/004/01.01.01\_60/gr\_QSC004v010101p.pdf
https://nvlpubs.nist.gov/nistpubs/ir/2017/NIST.IR.8183.pdf
https://www.iiconsortium.org/pdf/IIC\_PUB\_G4\_V1.00\_PB.pdf
https://www.iso.org/standard/54534.html
https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf
https://www.iso.org/standard/54533.html
https://www.huawei.com/minisite/iot/img/hw\_iot\_secutity\_white\_paper\_2017\_en\_v2.pdf
https://webstore.iec.ch/publication/7030 & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
148 & IoTSF & requirement & 2.4.10.1 & Where the product or service provides a web based user interface, Strong Authentication is used. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
149 & IoTSF & requirement & 2.4.10.13 & Administration Interfaces are accessible only by authorized operators. Mutual Authentication is used over administration interfaces, for example, by using certificates. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
150 & IoTSF & requirement & 2.4.10.14 & Reduce the lifetime of sessions to mitigate the risk of session hijacking and replay attacks. For example to reduce the time an attacker has to capture a session cookie and use it to access an application. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
151 & IoTSF & requirement & 2.4.10.15 & All inputs and outputs are checked for validity e.g. use “Fuzzing” tests to check for acceptable responses or output for both expected (valid) and unexpected (invalid) input stimuli. & M & 1 & Business & Process & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
152 & IoTSF & requirement & 2.4.10.3 & Where the product or service provides a web based management interface, Strong Authentication is used to the web server. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
153 & IoTSF & requirement & 2.4.10.4 & Where a web user interface password is used for login authentication, the initial password or factory reset password is unique to each device in the product family. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
154 & IoTSF & requirement & 2.4.10.5 & The web user interface is protected by an automatic session idle logout timeout function. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
155 & IoTSF & requirement & 2.4.10.6 & User passwords are not stored in plain text Strong passwords are required, and a random salt value is incorporated with the password. For further info see the 3GPP TS33.117 Password policy [ref 17], NIST SP800-63b [ref 26] and NCSC [ref 48]. & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
156 & IoTSF & requirement & 2.4.10.7 & Where passwords are entered on a user & M & 1 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
157 & IoTSF & requirement & 2.4.10.8 & The web user interface shall follow good practice guidelines, such as those listed in the OWASP [Ref 30]. & M & 1 & Business & Policy & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
158 & IoTSF & requirement & 2.4.10.9 & A vulnerability assessment has been performed before deployment and on an ongoing basis afterwards. & M & 1 & Business & Process & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
159 & IoTSF & requirement & 2.4.11.1 & Where an application’s user interface password is used for login authentication, the initial password or factory reset password is unique to each device in the product family. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
160 & IoTSF & requirement & 2.4.11.2 & Password entry follows industry standard practice such recommendations of the 3GPP TS33.117 Password policy [ref 17] or NIST SP800-63b [ref 26]. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
161 & IoTSF & requirement & 2.4.11.3 & The mobile application ensures that any related databases or files are either tamper resistant or restricted in their access. Upon detection of tampering of the databases or files they are reinitialised. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
162 & IoTSF & requirement & 2.4.11.4 & Where the application communicates with a product related remote server(s), or device, it does so over a secure connection such as a TLS connection using certificate pinning. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
163 & IoTSF & requirement & 2.4.11.5 & The product securely stores any passwords using an industry standard cryptographic algorithm, for example see FIPS 140-2 [ref 5]. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
164 & IoTSF & requirement & 2.4.11.6 & Where passwords are entered on a user interface, the actual pass phrase is obscured by default to prevent the capture of passwords. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
165 & IoTSF & requirement & 2.4.11.8 & Secure administration interfaces: it is important that configuration management functionality is accessible only by authorised operators and administrators. Enforce strong authentication over administration interfaces, for example, by using certificates. & M & 1 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
166 & IoTSF & requirement & 2.4.12.11 & The supplier or manufacturer of any devices and/or services shall provide information about how the device(s) removal and/or disposal shall be carried out to maintain the end user’s privacy and security. & M & 1 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
167 & IoTSF & requirement & 2.4.12.12 & The supplier or manufacturer of any devices or services shall provide clear information about the end user’s responsibilities to maintain the devices and/or services privacy and security. & M & 1 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
168 & IoTSF & requirement & 2.4.12.2 & The product/service ensures that all Personal Information is encrypted (both when stored and if communicated out of the device, see IoTSF guidance [ref 44] Part H on Network Connections & M & 1 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
169 & IoTSF & requirement & 2.4.12.5 & The Product Manufacturer or Service Provider shall ensure that a data retention policy is in place and documented for users. & M & 1 & Business & Policy & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
170 & IoTSF & requirement & 2.4.12.6 & There is a method or methods for the product owner to be informed about what Personal Information is collected, why, where it will be stored. & M & 1 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
171 & IoTSF & requirement & 2.4.13.11 & All the related servers and network elements prevent the use of null or blank passwords. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
172 & IoTSF & requirement & 2.4.13.14 & All the related servers and network elements enforce passwords that follows industry standard practice such recommendations of the 3GPP TS33.117 Password policy [ref 17], NIST SP800-63b [ref 26] and NCSC guidance [ref 48]. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
173 & IoTSF & requirement & 2.4.13.15 & The maximum permissible number of consecutive failed user account login attempts follows the recommendations of 3GPP TS33.117 password policy [ref 17]. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
174 & IoTSF & requirement & 2.4.13.16 & All the related servers and network elements store any passwords using a cryptographic implementation using industry standard cryptographic algorithms, for example see FIPS 140-2 [ref 5]. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
175 & IoTSF & requirement & 2.4.13.17 & All the related servers and network elements support access control measures to restrict access to sensitive information or system processes to privileged accounts. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
176 & IoTSF & requirement & 2.4.13.18 & All the related servers and network elements prevent anonymous/guest access except for read only access to public information. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
177 & IoTSF & requirement & 2.4.13.2 & Any product related web servers have their webserver identification options (e.g. Apache or Linux) switched off. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
178 & IoTSF & requirement & 2.4.13.21 & Where a Product or Service includes any safety critical or life-impacting functionality, the services infrastructure shall incorporate redundancy to ensure service continuity and availability. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
179 & IoTSF & requirement & 2.4.13.22 & Input data validation should be maintained in accordance with industry practiced methods as per NIST 800-53 SI-10 [Ref 33]. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
180 & IoTSF & requirement & 2.4.13.23 & If run as a cloud service, the cloud service TCP based communications (such as MQTT connections) are encrypted and authenticated using the latest TLS standard. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
181 & IoTSF & requirement & 2.4.13.24 & If run as a cloud service, UDP-based communications are encrypted using the latest Datagram Transport Layer Security (DTLS). & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
182 & IoTSF & requirement & 2.4.13.3 & All product related web servers have their webserver HTTP trace and trace methods disabled. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
183 & IoTSF & requirement & 2.4.13.4 & All the product related web servers’ TLS certificate(s) are signed by trusted certificate authorities; are within their validity period; and processes are in place for their renewal. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
184 & IoTSF & requirement & 2.4.13.5 & The Product Manufacturer or Service Provider has a process to monitor the relevant security advisories to ensure all the product related web servers use protocols with no publicly known weaknesses. & M & 1 & Business & Process & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
185 & IoTSF & requirement & 2.4.13.7 & The product related web servers have repeated renegotiation of TLS connections disabled. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
186 & IoTSF & requirement & 2.4.13.8 & The related servers have unused IP ports disabled. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
187 & IoTSF & requirement & 2.4.13.9 & Where a product related to a webserver encrypts communications using TLS and requests a client certificate, the server(s) only establishes a connection if the client certificate and its chain of trust are valid. & M & 1 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
188 & IoTSF & requirement & 2.4.14.3 & In manufacture, all the devices are logged by the product vendor, utilising unique tamper resistant identifiers such as serial number so that cloned or duplicated devices can be identified and either disabled or prevented from being used with the system. & M & 1 & Business & process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
189 & IoTSF & requirement & 2.4.14.4 & The production system for a device has a process to ensure that any devices with duplicate serial numbers are not shipped and are either reprogrammed or destroyed. & M & 1 & Business & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
190 & IoTSF & requirement & 2.4.14.7 & A cryptographic protected ownership proof shall be transferred along the supply chain and extended if a new owner is added in the chain. This process shall be based on open standards like Enhanced Privacy ID, Certificates per definition in ISO 20008/20009 [ref 42]. & M & 1 & Business & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
191 & IoTSF & requirement & 2.4.15.1 & The configuration of the device and any related web services is tamper resistant i.e. sensitive configuration parameters should only be changeable by authorised people (evidence should list the parameters and who is authorised to change). & M & 1 & Business & \textit{NULL} & 2.4.15 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
192 & IoTSF & requirement & 2.4.15.2 & The configuration shall be provisioned to the device just in time by authorised services, to replace any existing pre-configuration for secure operation. & M & 1 & Business & Process & 2.4.15 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
193 & IoTSF & requirement & 2.4.16.1 & Where a device or devices are capable of having their ownership transferred to a different owner, all the previous owner’s Personal Information shall be removed from the device(s) and registered services. This option must be available when a transfer of ownership occurs or when an end user wishes to delete their Personal Information from the service or device. & M & 1 & Business & Process & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
194 & IoTSF & requirement & 2.4.16.2 & Where a device or devices user wishes to end the service, all Personal Information shall be removed from the device and related services. & M & 1 & Business & Process & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
195 & IoTSF & requirement & 2.4.16.5 & The device registration [ref 16] with the Service Provider shall be secure (method and reasoning needed in evidence). & M & 1 & Business & Process & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
196 & IoTSF & requirement & 2.4.16.6 & The device manufacturer ensures that the identity of the device is independent of the end user, to ensure anonymity and comply with relevant local data privacy laws e.g. GDPR [ref 14] in the EU. & M & 1 & Business & Policy & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
197 & IoTSF & requirement & 2.4.3.21 & There is a point of contact for third party suppliers with security issues. & M & 1 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
198 & IoTSF & requirement & 2.4.4.1 & The product’s processor system has an irrevocable hardware Secure Boot process. & M & 1 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
199 & IoTSF & requirement & 2.4.4.13 & In production devices the microcontroller/ microprocessor(s) shall not allow the firmware to be read out of the products nonvolatile [FLASH] memory. Where a separate non-volatile memory device is used the contents shall be encrypted. & M & 1 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
200 & IoTSF & requirement & 2.4.4.4 & The Secure Boot process is enabled by default. & M & 1 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
201 & IoTSF & requirement & 2.4.4.5 & Any debug interface (for example, I/O ports such as JTAG) only communicates with authorised and authenticated entities on the production devices. & M & 1 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
202 & IoTSF & requirement & 2.4.4.6 & The hardware incorporates protection against tampering and this has been enabled. The level of tamper protection must be determined by the risk assessment. & M & 1 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
203 & IoTSF & requirement & 2.4.5.15 & The software must be architected to identify and ring fence sensitive software components, including cryptographic processes, to aid inspection, review and test. The access from other software components must be controlled and restricted to known and acceptable operations. For example, security related processes should be executed at higher privilege levels in the application processor hardware. & M & 1 & Business System & Process Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
204 & IoTSF & requirement & 2.4.6.10 & All the applicable security features supported by the OS are enabled. & M & 1 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
205 & IoTSF & requirement & 2.4.6.5 & If passwords absolutely must be stored in a local file, then passwords file(s) are owned by and are only accessible to and writable by the by the Devices’ OS’s most privileged account. & M & 1 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
206 & IoTSF & requirement & 2.4.6.8 & The product’s OS kernel and its functions are prevented from being called by external product level interfaces and unauthorised applications. & M & 1 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
207 & IoTSF & requirement & 2.4.7.1 & The product prevents unauthorised connections to it or other devices the product is connected to. For example, there is a firewall on each interface and internet layer protocol. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
208 & IoTSF & requirement & 2.4.7.10 & For any Wi-Fi connection WPA2 [ref 51], or later versions with AES, or a similar strength encryption has been used and insecure protocols such as WPA and TKIP are disabled & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
209 & IoTSF & requirement & 2.4.7.11 & Where WPA2 WPS is used it has a unique, random key per device and enforces exponentially increasing retry attempt delays. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
210 & IoTSF & requirement & 2.4.7.12 & All network communications keys are stored securely, in accordance with industry standards such as FIPS 140-2 [ref 5] or similar. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
211 & IoTSF & requirement & 2.4.7.13 & Where a TCP protocol, such as MQTT, is used, it is protected by a TLS connection with no known vulnerabilities. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
212 & IoTSF & requirement & 2.4.7.14 & Where a UDP protocol is used, such as CoAP, it is protected by a DTLS connection with no known vulnerabilities. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
213 & IoTSF & requirement & 2.4.7.15 & Where cryptographic suites are used such as TLS, all cipher suites shall be listed and validated against the current security recommendations such as NIST 800-131A [ref 2] or OWASP. Where insecure ciphers suites are identified they shall be removed from the product. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
214 & IoTSF & requirement & 2.4.7.16 & All use of cryptography by the product, such as TLS cipher suites, shall be listed and validated against the import/export requirements for the territories where the product is to be sold and/or shipped. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
215 & IoTSF & requirement & 2.4.7.18 & The product only enables the communications interfaces, network protocols, application protocols and network services necessary for the product’s operation. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
216 & IoTSF & requirement & 2.4.7.19 & Communications protocols should be latest versions with no publically known vulnerabilities and/or appropriate for the product. & M & 1 & Business & Policy & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
217 & IoTSF & requirement & 2.4.7.2 & The network component and firewall (if applicable) configuration has been reviewed and documented for the required/defined secure behaviour. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
218 & IoTSF & requirement & 2.4.7.20 & Post product launch communications protocols should be maintained throughout the product life cycle to the most secure versions available with no publically known vulnerabilities. & M & 1 & Business & Policy & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
219 & IoTSF & requirement & 2.4.7.21 & If a factory reset is made, the device should warn that secure operation may be compromised unless updated. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
220 & IoTSF & requirement & 2.4.7.3 & In products with network interfaces, to stop bridging of security domains, the uncontrolled, and any unintended packet forwarding functions should be blocked to stop undesirable communication paths. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
221 & IoTSF & requirement & 2.4.7.4 & Devices support only the versions of application layer protocols with no publically known vulnerabilities. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
222 & IoTSF & requirement & 2.4.7.6 & All the products unused ports are closed and only the required ports are active. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
223 & IoTSF & requirement & 2.4.7.7 & If a connection requires a password or passcode or passkey for connection authentication, the factory issued or reset password is unique to each device. Examples are Wi-Fi access passwords and Bluetooth PINS. & M & 1 & Business & Process & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
224 & IoTSF & requirement & 2.4.7.8 & Where using initial pairing process, a Strong Authentication shall be used; requiring physical interaction with the device or possession of a shared secret. For example, Bluetooth Numeric Comparison [ref 38]. & M & 1 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
225 & IoTSF & requirement & 2.4.7.9 & Where a wireless interface has an initial pairing process, the passkeys are changed from the factory issued, or reset password prior to providing normal service. & M & 1 & Business & Policy & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
226 & IoTSF & requirement & 2.4.8.1 & The product contains a unique and tamperresistant device identifier (e.g. the chip serial number or other unique silicon identifier) for example binding code and data to a specific device hardware. This is to mitigate threats from cloning. & M & 1 & System & Hardware & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
227 & IoTSF & requirement & 2.4.8.10 & The access control privileges are defined, justified and documented. & M & 1 & Business & Process & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
228 & IoTSF & requirement & 2.4.8.11 & The product only allows controlled user account access; access using anonymous or guest user accounts is not supported without justification. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
229 & IoTSF & requirement & 2.4.8.14 & If the product has a password recovery or reset mechanism, an assessment has been made to confirm that this mechanism cannot readily be abused by an unauthorised party. & M & 1 & Business & Process & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
230 & IoTSF & requirement & 2.4.8.15 & Where passwords are entered on a user interface, the actual pass phrase is obscured by default. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
231 & IoTSF & requirement & 2.4.8.3 & Where a user interface password is used for login authentication, the factory issued or reset password is unique to each device in the product family. If a password-less authentication is used the same principles of uniqueness apply. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
232 & IoTSF & requirement & 2.4.8.4 & The product does not accept the use of null or blank passwords. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
233 & IoTSF & requirement & 2.4.8.5 & The product will not allow new passwords containing the user account name with which the user account is associated. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
234 & IoTSF & requirement & 2.4.8.6 & Password entry follows industry standard practice such recommendations of the 3GPP TS33.117 Password policy [ref 17], NIST SP800-63b [ref 26] or NCSC [ref 48] on password length, characters from the groupings and special characters. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
235 & IoTSF & requirement & 2.4.8.7 & The product has defence against brute force repeated login attempts, such as exponentially increasing retry attempt delays. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
236 & IoTSF & requirement & 2.4.8.8 & The product securely stores any passwords using an industry standard cryptographic algorithm, compliant with an industry standard such as NIST SP800-63b [ref 26] or similar. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
237 & IoTSF & requirement & 2.4.8.9 & The product supports access control measures to the root/highest privilege account to restrict access to sensitive information or system processes. & M & 1 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
238 & IoTSF & requirement & 2.4.9.4 & There is a secure method of key insertion that protects keys against copying. & M & 1 & System & Software & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
239 & IoTSF & requirement & 2.4.9.5 & All the product related cryptographic functions have no publicly known unmitigated weaknesses, for example MD5 and SHA-1 are not used, e.g. those stipulated in NIST SP800-131A [ref 2]. & M & 1 & Business & Process & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
240 & IoTSF & requirement & 2.4.9.6 & All the product related cryptographic functions have no publicly known unmitigated weaknesses, for example MD5 and SHA-1 are not used, e.g. those stipulated in NIST SP800-131A [ref 2]. & M & 1 & Business & Process & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
241 & IoTSF & requirement & 2.4.9.7 & The product stores all sensitive unencrypted parameters, e.g. keys, in a secure, tamperresistant location. & M & 1 & System & Hardware & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
242 & IoTSF & requirement & 2.4.13.1 & All the product related cloud and network elements have the latest operating system(s) security updates implemented and processes are in place to keep them updated. & M & 2 & Business & Process & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
243 & IoTSF & requirement & 2.4.13.20 & Where a Product or Services includes any safety critical or life-impacting functionality, the services infrastructure shall incorporate protection against DDOS attacks, such as dropping of traffic or sink-holing. See NIST SP 800-53 SC-5 [ref 32]. & M & 2 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
244 & IoTSF & requirement & 2.4.13.26 & Product-related cloud services bind API keys to specific IoT applications and are not installed on non-authorised devices. & M & 2 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
245 & IoTSF & requirement & 2.4.13.28 & If run as a cloud service, privileged roles are defined and implemented for any gateway/service that can configure devices. & M & 2 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
246 & IoTSF & requirement & 2.4.13.33 & Product-related cloud services monitor for compliance with connection policies and report out-of-compliance connection attempts. & M & 2 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
247 & IoTSF & requirement & 2.4.16.3 & The Service Provider should not have the ability to do a reverse lookup of device ownership from the device identity. & M & 2 & Business & Process & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
248 & IoTSF & requirement & 2.4.3.18 & Where real-time or up-time expectations are present, a procedure must be defined for notifying connected components of impending downtime for updates. & M & 2 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
249 & IoTSF & requirement & 2.4.3.19 & Responsibility is allocated for each stage of the update process. & M & 2 & Business & Responsibility & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
250 & IoTSF & requirement & 2.4.3.20 & Responsibility is allocated for control, logging and auditing of the update process. & M & 2 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
251 & IoTSF & requirement & 2.4.3.22 & Where remote update is supported, there is an established process/plan for validating "updates" and updating devices on an on-going or remedial basis e.g. guidance on software updates is available from the IoTSF Best Practice Guidelines Part L [ref 44]. & M & 2 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
252 & IoTSF & requirement & 2.4.3.23 & The security update policy for devices with a constrained power source shall be assessed to balance the needs of maintaining the integrity and availability of the device. & M & 2 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
253 & IoTSF & requirement & 2.4.3.24 & There is a named owner responsible for assessing third party supplied components (hardware and software) used in the product e.g. The OS suppliers provided a completed IoTSF Framework Compliance Checklist [ref 19], document or equivalent. & M & 2 & Business & Role & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
254 & IoTSF & requirement & 2.4.3.25 & Where a remote software upgrade can be supported by the device, there should be a transparent and auditable policy with schedule of actions to fix any vulnerabilities found. & M & 2 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
255 & IoTSF & requirement & 2.4.3.4 & The company follows industry standard cyber security recommendations (e.g. UK Cyber Essentials, NIST Cyber Security Framework, ISO27000 etc.). & M & 2 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
256 & IoTSF & requirement & 2.4.3.6 & A policy has been established for addressing risks that could impact security and affect or involve technology or components incorporated into the product or service provided. & M & 2 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
257 & IoTSF & requirement & 2.4.4.10 & All the product’s development test points are securely disabled or removed wherever possible in production devices. & M & 2 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
258 & IoTSF & requirement & 2.4.4.11 & Tamper Evident measures have been used to identify any interference to the assembly to the end user. & M & 2 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
259 & IoTSF & requirement & 2.4.4.17 & The product shall have a hardware source for generating true random numbers. & M & 2 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
260 & IoTSF & requirement & 2.4.4.2 & The product’s processor system has an irrevocable “Trusted Root Hardware Secure Boot”. & M & 2 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
261 & IoTSF & requirement & 2.4.4.8 & The hardware incorporates physical protection against reverse engineering. The level of protection must be determined by the risk assessment. & M & 2 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
262 & IoTSF & requirement & 2.4.5.11 & Development software versions have any debug functionality switched off if the software is operated on the product outside of the product vendor’s trusted environment. & M & 2 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
263 & IoTSF & requirement & 2.4.5.13 & The product’s software source code follows the basic good practice of a Language subset (e.g. MISRA-C) coding standard. & M & 2 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
264 & IoTSF & requirement & 2.4.5.14 & The product’s software source code follows the basic good practice of static vulnerability analysis [ref 37] by the developer. & M & 2 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
265 & IoTSF & requirement & 2.4.5.17 & The build environment and toolchain used to compile the application is run on a build system with controlled and auditable access. & M & 2 & Business & Policy Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
266 & IoTSF & requirement & 2.4.5.18 & The build environment and toolchain used to create the software is under configuration management and version control, and its integrity is validated regularly. & M & 2 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
267 & IoTSF & requirement & 2.4.5.20 & The production software signing keys are stored and secured in a storage device compliant to FIPS-140-2 level 2 [ref 5], or equivalent or higher standard. & M & 2 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
268 & IoTSF & requirement & 2.4.5.21 & Where the device software communicates with a product related webserver or application over TCP/IP or UDP/IP, the device software uses certificate pinning or public/private key equivalent, where appropriate. & M & 2 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
269 & IoTSF & requirement & 2.4.5.23 & All inputs and outputs are checked for validity e.g. use “Fuzzing” tests to check for acceptable responses or output for both expected (valid) and unexpected (invalid) input stimuli. & M & 2 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
270 & IoTSF & requirement & 2.4.5.24 & The software has been designed to meet the safety requirements identified in the risk assessment; for example in the case of unexpected invalid inputs, or erroneous software operation, the product does not become dangerous, or compromise security of other connected systems. & M & 2 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
271 & IoTSF & requirement & 2.4.5.33 & Memory locations used to store sensitive material (e.g. cryptographic keys, passwords/passphrases, etc.) are sanitised as soon as possible after they are no longer needed. These can include but are not limited to locations on the heap, the stack, and statically-allocated storage [ref 47]. & M & 2 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
272 & IoTSF & requirement & 2.4.5.4 & If remote software upgrade is supported by a device, software images shall be encrypted whilst being transferred to it. & M & 2 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
273 & IoTSF & requirement & 2.4.5.5 & If the product has any virtual port(s) that are not required for normal operation, they are only allowed to communicate with authorised and authenticated entities or securely disabled when shipped. Where a port is used for field diagnostics, the port input commands are deactivated and the output provides no information which could compromise the device, such as credentials, memory address or function names. & M & 2 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
274 & IoTSF & requirement & 2.4.6.12 & The OS implements a separation architecture to separate trusted from untrusted applications & M & 2 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
275 & IoTSF & requirement & 2.4.6.13 & The product’s OS kernel is designed such that each component runs with the minimal security capabilities required (e.g. a microkernel architecture). & M & 2 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
276 & IoTSF & requirement & 2.4.9.10 & All key lengths are sufficient for the level of assurance required such as detailed in NIST SP800-57 Part 1. & M & 2 & Business & Policy & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
277 & IoTSF & requirement & 2.4.9.3 & There is a process for secure provisioning of keys that includes generation, distribution, update, revocation and destruction. For example in compliance with FIPS140-2 [ref 5] or a similar process. & M & 2 & Business & Process & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
278 & IoTSF & requirement & 2.4.9.9 & In device manufacture, all asymmetric encryption private keys that are unique to each device are secured as outlined in FIPS 140-2[ref 5].They must be truly randomly internally generated or securely programmed into each device. & M & 2 & Business & Process & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
279 & IoTSF & requirement & 2.4.3.13 & As part of the Security Policy, develop a conflict resolution process for Vulnerability Disclosures. & M & 3 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
280 & IoTSF & requirement & 2.4.4.3 & The product’s processor system has a measured irrevocable hardware Secure Boot process. & M & 3 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
281 & IoTSF & requirement & 2.4.4.7 & The hardware incorporates physical protection against tampering to reduce the attack surface. The level of protection must be determined by the risk assessment. & M & 3 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
282 & IoTSF & requirement & 2.4.5.34 & Any caches which potentially store sensitive material are cleared / flushed after memory locations containing sensitive material have been sanitised. & M & 3 & System & Hardware & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
283 & IoTSF & requirement & 2.4.16.4 & In case of ownership change, the device has an irrevocable method of decommissioning and recommissioning. & M & 1 & system & process & 2.4.16 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
284 & IoTSF & requirement & 2.4.5.9 & There are measures to prevent the installation of non-production software onto production devices. & M & 0 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
285 & IoTSF & requirement & 2.4.5.12 & Steps have been taken to protect the products’ software from sensitive information leakage and side-channel attacks. & M & 0 & System & Software Hardware & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
286 & IoTSF & requirement & 2.4.10.10 & All data being transferred over interfaces should be validated where appropriate. This could include checking the data type, length, format, range, authenticity, origin and frequency. & M & 0 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
287 & IoTSF & requirement & 2.4.10.11 & Sanitize input in Web applications by using URL encoding or HTML encoding to wrap data and treat it as literal text rather than executable script. & M & 0 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
288 & IoTSF & requirement & 2.4.10.12 & All inputs and outputs are validated using for example a whitelist containing authorised origins of data and valid attributes of such data. & M & 0 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
289 & IoTSF & requirement & 2.4.10.2 & Where the product or service provides a web based interface, public and restricted areas shall be separated for authentication. & M & 0 & System & Software & 2.4.10 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
290 & IoTSF & requirement & 2.4.11.7 & All data being transferred over interfaces should be validated where appropriate. This could include checking the data type, length, format, range, authenticity, origin and frequency. & M & 0 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
291 & IoTSF & requirement & 2.4.11.9 & All application inputs and outputs are validated using for example a whitelist containing authorised origins of data and valid attributes of such data, see NIST SP 800-167 [ref 34]. & M & 0 & System & Software & 2.4.11 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
292 & IoTSF & requirement & 2.4.12.1 & The product/service stores the minimum amount of Personal Information from users required for the operation of the service. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
293 & IoTSF & requirement & 2.4.12.10 & The supplier or manufacturer of any devices or devices shall provide clear information about how the device(s) shall be setup to maintain the end user’s privacy and security. & M & 0 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
294 & IoTSF & requirement & 2.4.12.13 & Security of devices and services should be designed with usability in mind. Reducing user decision points that may have a detrimental impact on security and privacy. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
295 & IoTSF & requirement & 2.4.12.14 & The product or service only records audio/visual data in accordance with the authorization of the user (e.g., no passive recording without explicit authorisation). & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
296 & IoTSF & requirement & 2.4.12.15 & The supplier or manufacturer performs a privacy impact assessment (PIA) to identify Personally Identifiable Information (PII) and design approaches for safeguarding user privacy [ref 49]. & A & 0 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
297 & IoTSF & requirement & 2.4.12.3 & The product/service ensures that only authorised personnel have access to personal data of users. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
298 & IoTSF & requirement & 2.4.12.4 & The product/service ensures that Personal Information is anonymised whenever possible and in particular in any reporting. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
299 & IoTSF & requirement & 2.4.12.7 & There is a method or methods for the product owner to check/verify what Personal Information is collected and deleted. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
300 & IoTSF & requirement & 2.4.12.8 & The product / service can be made compliant with the local and/or regional Personal Information protection legislation where the product is to be sold for example GDPR [ref 14]. & M & 0 & System & Software & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
301 & IoTSF & requirement & 2.4.12.9 & The supplier or manufacturer of any device shall provide information about how the device(s) functions within the end user’s network may affect their privacy. & A & 0 & Business & Process & 2.4.12 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
302 & IoTSF & requirement & 2.4.13.10 & Where a product related to a webserver encrypts communications using TLS, certificate pinning is implemented. For example, using OWASP [ref 31] or similar organisations’ certificate and public key pinning guidance. & A & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
303 & IoTSF & requirement & 2.4.13.19 & If run as a cloud service, the service meets industry standard cloud security principles such as the Cloud Security Alliance [ref 18], NIST Cyber Security Framework [ref 21] or UK Government Cloud Security Principles [ref 24]. & A & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
304 & IoTSF & requirement & 2.4.13.25 & Where device identity and/or configuration registries (e.g. thing shadows) are implemented within a cloud service, the registries are configured to restrict access to only authorised administrators. & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
305 & IoTSF & requirement & 2.4.13.27 & Product-related cloud services API keys are not hard-coded into devices or applications. & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
306 & IoTSF & requirement & 2.4.13.29 & Product-related cloud service databases are encrypted during storage. & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
307 & IoTSF & requirement & 2.4.13.30 & Product-related cloud service databases restrict read/write access to only authorized individuals, devices and services. & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
308 & IoTSF & requirement & 2.4.13.31 & Product-related cloud services are designed using a defence-in-depth architecture consisting of Virtual Private Clouds (VPCs), firewalled access, and cloud-based monitoring. & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
309 & IoTSF & requirement & 2.4.13.32 & When implemented as a cloud service, all remote access to cloud services is via secure means (e.g., SSH). & M & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
310 & IoTSF & requirement & 2.4.13.34 & IoT devices should connect to cloud services using edge-to-cloud secure hardware (e.g., zero-touch provisioning). & A & 0 & System & Hardware & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
311 & IoTSF & requirement & 2.4.13.6 & The product related web servers support appropriately secure TLS/DTLS ciphers and disable/remove support for deprecated ciphers. For example see guidance at ENISA [ref 27], SSL Labs [ref 29], IETF RFC7525 [ref 28] and NCSC [ref 50]. & A & 0 & System & Software & 2.4.13 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
312 & IoTSF & requirement & 2.4.14..8 & An auditable manifest of all libraries used within the product (open source, etc.) to support informed vulnerability management during deployment is maintained. & A & 0 & Business & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
313 & IoTSF & requirement & 2.4.14.1 & The product has the entire production test and calibration software used during manufacture erased or removed or secured before the product is dispatched from the factory. This is to prevent alteration of the product post manufacture when using authorised production software, for example hacking of the RF characteristics for greater RF ERP. Where such functionality is required in a service centre, it shall be erased or removed upon completion of any servicing activities. & A & 0 & System & Software & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
314 & IoTSF & requirement & 2.4.14.2 & Any hardware design files, software source code and final production software images with full descriptive annotations are stored encrypted in off-site locations or by a 3party Escrow service. & A & 0 & Business & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
315 & IoTSF & requirement & 2.4.14.5 & Where a product includes a trusted Secure Boot process, the entire production test and any related calibration is executed with the processor system operating in its secured boot, authenticated software mode. & A & 0 & System & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
316 & IoTSF & requirement & 2.4.14.6 & A securely controlled area and process shall be used for device provisioning where the production facility is untrusted. For example, implements the controls required in Common Criteria EAL5+/6 certification [refs 6, 7, 8 and 9]. & A & 0 & Business & Process & 2.4.14 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
317 & IoTSF & requirement & 2.4.3.1 & There is a person or role, typically a board level executive, who takes ownership of and is responsible for product, service and business level security. & M & 0 & Business & Responsibility & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
318 & IoTSF & requirement & 2.4.3.10 & A security threat and risk assessment shall have been carried out using a standard methodology such as OWASP, Octave or NIST RMF Risk Management Framework [ref 35] to determine the risks and evolving threats before a design is started. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
319 & IoTSF & requirement & 2.4.3.11 & As part of the Security Policy, develop specific contact web pages for Vulnerability Disclosure reporting. & M & 0 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
320 & IoTSF & requirement & 2.4.3.12 & As part of the Security Policy, provide a dedicated security email address and/or secure online page for Vulnerability Disclosure communications. & M & 0 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
321 & IoTSF & requirement & 2.4.3.14 & As part of the Security Policy, publish the organisation’s conflict resolution process for Vulnerability Disclosures. & A & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
322 & IoTSF & requirement & 2.4.3.15 & As part of the Security Policy, develop response steps and performance targets for Vulnerability Disclosures. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
323 & IoTSF & requirement & 2.4.3.16 & As part of the Security Policy, develop security advisory notification steps. For examples see US Cert programme [ref 46]. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
324 & IoTSF & requirement & 2.4.3.17 & The Security Policy shall be compliant with ISO 30111 or similar standard. & A & 0 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
325 & IoTSF & requirement & 2.4.3.2 & There is a person or role, who takes ownership for adherence to this compliance checklist process. & M & 0 & Business & Responsibility & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
326 & IoTSF & requirement & 2.4.3.5 & A policy has been established for interacting with both internal and third party security researcher(s) on the products or services. & M & 0 & Business & Policy & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
327 & IoTSF & requirement & 2.4.3.7 & Processes and plans are in place based upon the IoTSF Vulnerability Disclosure Guidelines [ref 19], or a similar recognised process, to deal with the identification of a security vulnerability or compromise when they occur. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
328 & IoTSF & requirement & 2.4.3.8 & A process is in place for consistent briefing of senior executives in the event of the identification of a vulnerability or a security breach, especially those executives who may deal with the media or make public announcements. In particular, that any public statements made in the event of a security breach should give as full and accurate an account of the facts as possible. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
329 & IoTSF & requirement & 2.4.3.9 & There is a secure notification process based upon the IoTSF Vulnerability Disclosure Guidelines [ref 19] or a similar recognised process, for notifying partners/users of any security updates. & M & 0 & Business & Process & 2.4.3 & 5.2-2 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
330 & IoTSF & requirement & 2.4.4.14 & Where the products’ credential/key storage is external to its processor, the storage and processor shall be cryptographically paired to prevent the credential/key storage being used by unauthorised software. & M & 0 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
331 & IoTSF & requirement & 2.4.4.15 & Where production devices have a CPU watchdog, it is enabled and will reset the device in the event of any unauthorised attempts to pause or suspend the CPU’s execution. & M & 0 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
332 & IoTSF & requirement & 2.4.4.16 & Where the product has a hardware source for generating true random numbers, it is used for all relevant cryptographic operations including nonce, initialisation vector and key generation algorithms. For guidance see: NIST SP 800-90A [ref 3]. & M & 0 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
333 & IoTSF & requirement & 2.4.4.9 & All communications port(s), such as USB, RS232 etc., which are not used as part of the product’s normal operation are not physically accessible or only communicate with authorised and authenticated entities. & M & 0 & System & Hardware & 2.4.4 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
334 & IoTSF & requirement & 2.4.5.1 & The product has measures to prevent unauthenticated software and files being loaded onto it. In the event that the product is intended to allow un-authenticated software, such software should only be run with limited permissions and/or in a sandbox. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
335 & IoTSF & requirement & 2.4.5.10 & Production software images shall be compiled in such a way that all unnecessary debug and symbolic information is removed, to prevent accidental release of superfluous data. & M & 0 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
336 & IoTSF & requirement & 2.4.5.16 & Software source code is developed, tested and maintained following defined repeatable processes. & M & 0 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
337 & IoTSF & requirement & 2.4.5.19 & Where present, production software signing keys are under access control. & M & 0 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
338 & IoTSF & requirement & 2.4.5.2 & Where remote software updates can be supported by the device, the software images are digitally signed by an approved signing authority. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
339 & IoTSF & requirement & 2.4.5.22 & For devices with no possibility of a software update, the conditions for and period of replacement support should be clear. & M & 0 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
340 & IoTSF & requirement & 2.4.5.25 & Support for partially installing updates is provided for devices whose on-time is insufficient for the complete installation of a whole update. & A & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
341 & IoTSF & requirement & 2.4.5.26 & Support for partially downloading updates is provided for devices whose network access is limited or sporadic. & A & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
342 & IoTSF & requirement & 2.4.5.27 & Where real-time expectations of performance are present, update mechanisms must not interfere with meeting these expectations (e.g. by running update processes at low priority). & A & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
343 & IoTSF & requirement & 2.4.5.28 & Where a device doesn’t support secure boot, upon a firmware update the user data and credentials should be re-initialised. & M & 0 & System & Hardware Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
344 & IoTSF & requirement & 2.4.5.29 & Where a device cannot verify authenticity of updates itself (e.g. due to no cryptographic capabilities), only a local update by a physically present user is permitted and is their responsibility. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
345 & IoTSF & requirement & 2.4.5.3 & Where updates are supported the software update package has its digital signature, signing certificate and signing certificate chain verified by the device before the update process begins. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
346 & IoTSF & requirement & 2.4.5.30 & When a device cannot verify authenticity of updates itself, it shall be possible revert to the last known good configuration which was stored on the device before the update was attempted. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
347 & IoTSF & requirement & 2.4.5.31 & Cryptographic keys for update integrity protection and confidentiality are securely managed in accordance with industry standards such as FIPS 140-2 [ref 5]. & M & 0 & Business & Process & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
348 & IoTSF & requirement & 2.4.5.32 & There is secure provisioning of cryptographic keys for updates during manufacture in accordance with industry standards such as FIPS 140-2 [ref 5]. & M & 0 & Business & Process Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
349 & IoTSF & requirement & 2.4.5.35 & An end-of-life policy shall be published which explicitly states the minimum length of time for which a device will receive software updates and the reasons for the length of the support period. The need for each update should be made clear to users and an update should be easy to implement. & M & 0 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
350 & IoTSF & requirement & 2.4.5.36 & Where possible, software updates should be pushed for a period appropriate to the device. This period shall be made clear to a user when supplying the device. The supply chain partners should inform the user that an update is required. & M & 0 & Business & Policy & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
351 & IoTSF & requirement & 2.4.5.6 & To prevent the stalling or disruption of the device’s software operation, watchdog timer are present, and cannot be disabled. & M & 0 & System & Hardware Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
352 & IoTSF & requirement & 2.4.5.7 & The product’s software signing root of trust is stored in tamper-resistant memory. & M & 0 & System & Hardware & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
353 & IoTSF & requirement & 2.4.5.8 & The product has protection against unauthorised reversion of the software to an earlier and potentially less secure version. & M & 0 & System & Software & 2.4.5 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
354 & IoTSF & requirement & 2.4.6.1 & The OS is implemented with relevant security updates prior to release. & A & 0 & Business & Process & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
355 & IoTSF & requirement & 2.4.6.11 & The OS is separated from the application(s) and is only accessible via defined secure interfaces. & A & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
356 & IoTSF & requirement & 2.4.6.3 & All unnecessary accounts or logins have been disabled or eliminated from the software at the end of the software development process. E.g. Development or debug accounts. & A & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
357 & IoTSF & requirement & 2.4.6.4 & Files, directories and persistent data are set to minimum access privileges required to correctly function. & A & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
358 & IoTSF & requirement & 2.4.6.6 & All OS non-essential services have been removed from the product’s software, image or file systems. & A & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
359 & IoTSF & requirement & 2.4.6.7 & All OS command line access to the most privileged accounts has been removed from the OS. & A & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
360 & IoTSF & requirement & 2.4.6.9 & Applications are operated at the lowest privilege level possible and only have access to the resources they need as controlled through appropriate access control mechanisms. For example, Products with one or more network interfaces, the uncontrolled, and any unintended packet forwarding functions should be blocked. & M & 0 & System & Software & 2.4.6 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
361 & IoTSF & requirement & 2.4.7.17 & Where there is a loss of communications or availability it shall not compromise the local integrity of the device. & M & 0 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
362 & IoTSF & requirement & 2.4.7.24 & As far as reasonably possible, devices should remain operating and locally functional in the case of a loss of network connection and should recover cleanly in the case of restoration of a loss of power. Devices should be able to return to a network in a sensible state and in an orderly fashion, rather than in a massive scale reconnect. & M & 0 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
363 & IoTSF & requirement & 2.4.7.5 & If an unauthorised change is detected, the device should alert the consumer/administrator to an issue and should not connect to wider networks than those necessary to perform the alerting function. & M & 0 & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
364 & IoTSF & requirement & 2.4.8.12 & The product allows the factory issued or OEM login accounts to be disabled or erased or renamed when installed or commissioned. & A & 0 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
365 & IoTSF & requirement & 2.4.8.13 & The product supports having any or all of the factory default user login passwords altered when installed or commissioned. & M & 0 & Business & Process & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
366 & IoTSF & requirement & 2.4.8.16 & The product allows an authorised and complete factory reset and all of the device’s authorisation information. & A & 0 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
367 & IoTSF & requirement & 2.4.8.17 & Where the product has the ability to remotely recover from attack, it should return to a known good state, to enable safe recovery and updating of the device. & M & 0 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
368 & IoTSF & requirement & 2.4.8.2 & Where the product has a secure source of time there is a method of validating its integrity, such as Secure NTP. & M & 0 & System & Software & 2.4.8 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
369 & IoTSF & requirement & 2.4.9.2 & If present, a true random number generator source has been validated for true randomness using an NIST SP800-22 [ref 4], FIPS 140-2 [ref 5] or a similar compliance process. & A & 0 & System & Hardware & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
370 & IoTSF & requirement & 2.4.9.8 & The cryptographic key chain used for signing production software is different from that used for any other test, development or other software images or support requirement. & A & 0 & System & Software & 2.4.9 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
371 & IoTSF & requirement & 2.4.7.22 & Where RF communications are enabled (e.g., ZigBee, etc.) antenna power is configured to limit ability of mapping assets to limit attacks such as WAR-Driving (see). & A & \textit{NULL} & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
372 & IoTSF & requirement & 2.4.7.23 & Protocol anonymity features are enabled in protocols (e.g., Bluetooth) to limit location tracking capabilities. & A & \textit{NULL} & System & Software & 2.4.7 & 5.1-1 & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} \\ \hline 
373 & OWASP ISVS & test & 5.1.9 & Verify that the platform provides protection against physical decapsulation, side channel and glitching attacks. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
374 & OWASP ISVS & test & 5.1.8 & Verify the chosen hardware has no unofficially documented debug features, such as special pin configurations that can enable or disable certain functionality. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
375 & OWASP ISVS & test & 5.1.7 & Verify that debugging headers are removed from PCBs. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
376 & OWASP ISVS & test & 5.1.6 & Verify that the platform security configuration of the platform can be locked. e.g. through burning OTP fuses. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
377 & OWASP ISVS & test & 5.1.5 & Verify that the platform provides memory and I/O protection capabilities so that only privileged processes can access certain resources. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
378 & OWASP ISVS & test & 5.1.4 & Verify that sensitive data such as private keys and certificates can be stored securely by leveraging dedicated hardware security features. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
379 & OWASP ISVS & test & 5.1.3 & Verify that cryptographic functions are provided by the platform. e.g. by leveraging dedicated functionality provided by the main chip or by external security chips. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
380 & OWASP ISVS & test & 5.1.2 & Verify that the platform supports validating the authenticity of the first stage bootloader. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
381 & OWASP ISVS & test & 5.1.10 & Verify descriptive silkscreens are removed from PCBs & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
382 & OWASP ISVS & test & 5.1.1 & Verify that the platform supports disabling or protecting access to debugging interfaces (e.g. JTAG, SWD). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
383 & OWASP ISVS & test & 4.4.4 & Verify that Wi-Fi Protected Setup (WPS) is not used to establish Wi-Fi connections between devices. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
384 & OWASP ISVS & test & 4.4.3 & Verify that in case WPA is used, it is used with AES encryption (CCMP mode). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
385 & OWASP ISVS & test & 4.4.2 & Verify that WPA2 or higher is used to protect Wi-Fi communications. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
386 & OWASP ISVS & test & 4.4.1 & Verify Wi-Fi connectivity is disabled unless required as part of device functionality. Devices with no need for network connectivity or which support other types of network connectivity, such as Ethernet, should have the Wi-Fi interface disabled. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
387 & OWASP ISVS & test & 4.3.7 & Verify the strongest Bluetooth Security Mode and Level supported by the device is used. For example, for Bluetooth 4.1 devices, Security Mode 4, Level 4 should be used to provide authenticated pairing and encryption. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
388 & OWASP ISVS & test & 4.3.6 & Verify the most secure Bluetooth pairing method available is used. Verify Out Of Band (OOB), Numeric Comparison, or Passkey Entry pairing methods are used depending on the communicating device's capabilities. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
389 & OWASP ISVS & test & 4.3.5 & Verify that encryption keys are the maximum allowable size. Bluetooth has configurable key size parameters for establishing a session, with configurations that allow keys of smaller size than the 16-32 byte size used by AES. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
390 & OWASP ISVS & test & 4.3.4 & Verify that for modern versions of Bluetooth, at least 6 digits are required for Secure Simple Pairing (SSP) authentication under all versions except “Just Works”. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
391 & OWASP ISVS & test & 4.3.3 & Verify devices that support for old versions of Bluetooth with simple modes of authentication require a PIN to pair devices. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
392 & OWASP ISVS & test & 4.3.2 & Verify that PIN or PassKey codes are not easily guessable. For example, verify PIN codes are not ‘0000’or ‘1234’. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
393 & OWASP ISVS & test & 4.3.1 & Verify that pairing and discovery is blocked in Bluetooth devices except when necessary. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
394 & OWASP ISVS & test & 4.2.7 & Verify certificates are favored over native username and passwords to authenticate MQTT transactions. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
395 & OWASP ISVS & test & 4.2.3 & Verify MQTT brokers only allow authorized IoT devices to subscribe and publish message topics. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
396 & OWASP ISVS & test & 4.2.2 & Verify that if shared secrets are used to cryptographically secure communication, that the same key is not hardcoded in each device or sensor. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
397 & OWASP ISVS & test & 4.2.1 & Verify that unencrypted communication is limited to data and instructions that are not of a sensitive nature. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
398 & OWASP ISVS & test & 4.1.7 & Verify that inter-chip communication is encrypted (e.g. Main board to daughter board communication). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
399 & OWASP ISVS & test & 4.1.6 & Verify that device's TLS implementation uses its own certificate store, pins to the endpoint certificate or public key, and disallows connections from endpoints with different certificates or key, even if signed by a trusted CA. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
400 & OWASP ISVS & test & 4.1.4 & Verify that for availability critical applications, either protection or detection of jamming is provided. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
401 & OWASP ISVS & test & 4.1.3 & Verify that in case TLS is used, the device cryptographically verifies the X.509 certificate. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
402 & OWASP ISVS & test & 4.1.2 & Verify that in case TLS is used, that its securely configured with FIPS-based cipher suites (or equivalent). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
403 & OWASP ISVS & test & 4.1.1 & Verify that communication with other components in the IoT ecosystem (including sensors, gateway and supporting cloud) occurs over a secure channel in which the confidentiality and integrity of data is guaranteed and in which protection against replay attacks is built into the communication protocol. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
404 & OWASP ISVS & test & 3.6.2 & Verify that only required kernel modules are enabled during runtime. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
405 & OWASP ISVS & test & 3.6.1 & Verify that loaded kernel modules are cryptographically signed and verified. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
406 & OWASP ISVS & test & 3.5.4 & Verify that deprecated insecure ciphers and hash functions (e.g. 3DES, MD5, SHA1) in new applications are not used, even if provided by the hardware security chip. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
407 & OWASP ISVS & test & 3.5.3 & Verify any default vendor keys used in bus encryption are replaced in production builds. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
408 & OWASP ISVS & test & 3.5.2 & Verify that keys (either secret or private) used to enable encryption on the serial bus are properly secured on the host. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
409 & OWASP ISVS & test & 3.5.1 & Verify that encryption is used on the bus between the security chip and other hardware components. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
410 & OWASP ISVS & test & 3.4.9 & Verify that encrypted firmware images are securely decrypted on the device. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
411 & OWASP ISVS & test & 3.4.8 & Verify that unsigned debug pre-production firmware builds can not be flashed onto devices. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
412 & OWASP ISVS & test & 3.4.7 & Verify that in the event of an update failure, the device reverts to a backup image or notifies the IoT ecosystem. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
413 & OWASP ISVS & test & 3.4.6 & Verify that the device cannot be downgraded to known vulnerable versions (anti-rollback). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
414 & OWASP ISVS & test & 3.4.5 & Verify that updates do not modify user-configured preferences, security, and/or privacy settings without notifying the user. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
415 & OWASP ISVS & test & 3.4.4 & Verify that the update process is not vulnerable to time-of-check time-of-use attacks (TOCTOU). This is generally accomplished by applying the update right after the authenticity of the update is validated. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
416 & OWASP ISVS & test & 3.4.3 & Verify that the authenticity of updates are cryptographically signed by a trusted source and verified before execution. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
417 & OWASP ISVS & test & 3.4.2 & Verify that devices can be updated automatically upon a pre-defined schedule. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
418 & OWASP ISVS & test & 3.4.11 & Verify that firmware updates are stored encrypted server-side. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
419 & OWASP ISVS & test & 3.4.10 & Verify that the device authenticates to the update server component prior to downloading the update. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
420 & OWASP ISVS & test & 3.4.1 & Verify that packages and user space applications use over the air updates decoupled from firmware updates. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
421 & OWASP ISVS & test & 3.3.6 & Verify the use of kernel security modules such as SELinux, AppArmor, GRSEC, and alike. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
422 & OWASP ISVS & test & 3.3.5 & Verify that SECure COMPuting (seccomp BPF) with filters are used and properly configured to only allow necessary system calls. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
423 & OWASP ISVS & test & 3.3.4 & Verify that Linux kernel capabilities are configured with a minimal set for processes that require elevated access. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
424 & OWASP ISVS & test & 3.3.2 & Verify that critical processes are configured to limit resources using control groups (cgroups). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
425 & OWASP ISVS & test & 3.3.1 & Verify that processes are isolated using Linux kernel namespaces. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
426 & OWASP ISVS & test & 3.2.9 & Verify the embedded OS provides protection against unauthorized access to RAM (e.g. RAM scrambling). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
427 & OWASP ISVS & test & 3.2.8 & Verify hardware level memory protection is used and privilege levels are enforced. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
428 & OWASP ISVS & test & 3.2.7 & Verify that memory protection controls such as Address Space Layout Randomization (ASLR) and Data Execution Prevention (DEP) are enabled by the embedded operating system. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
429 & OWASP ISVS & test & 3.2.6 & Verify that applications running on the device use the security features of the underlying operating system or kernel. Including cryptography, key storage, random number generation, authentication and authorization, logging, communications security. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
430 & OWASP ISVS & test & 3.2.5 & Verify that persistent filesystem storage volumes are encrypted. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
431 & OWASP ISVS & test & 3.2.4 & Verify that the OS kernel and software components are up to date and do not contain known vulnerabilities. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
432 & OWASP ISVS & test & 3.2.3 & Verify that the device does not make use of of legacy or insecure protocols such as Telnet and FTP. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
433 & OWASP ISVS & test & 3.2.2 & Verify that all network services exposed by the device on every network interface are necessary services and unnecessary services are removed or disabled. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
434 & OWASP ISVS & test & 3.2.11 & Verify that that third-party applications and services are configured to execute within a containerized runtime environment (e.g. LXC, Docker, etc.). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
435 & OWASP ISVS & test & 3.2.10 & Verify that an Integrity Measurement Architecture (IMA) is in use and appropriately configured. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
436 & OWASP ISVS & test & 3.2.1 & Verify that the embedded operating system is configured according to industry best practices, benchmarks, and uses secure defaults. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
437 & OWASP ISVS & test & 3.1.8 & Verify that Direct Memory Access (DMA) is not possible during boot. For example, ensure DMA is not possible via PCI connections. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
438 & OWASP ISVS & test & 3.1.7 & Verify that firmware is stored in an encrypted volume at rest. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
439 & OWASP ISVS & test & 3.1.6 & Verify that bootloader stages do not contain sensitive information (e.g. private keys or passwords logged to the console) as part of device start-up. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
440 & OWASP ISVS & test & 3.1.5 & Verify that the authenticity of next bootloader stages or application code is cryptographically verified during every step of the boot process. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
441 & OWASP ISVS & test & 3.1.4 & Verify that the authenticity of the first stage bootloader is verified by a trusted component of which the configuration in read-only memory (ROM) cannot be altered. e.g. CPU Based Secure Boot/Trusted Boot & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
442 & OWASP ISVS & test & 3.1.3 & Verify that communication interfaces such as, USB, UART, and other variants are disabled or adequately protected during every stage of the device's boot process. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
443 & OWASP ISVS & test & 3.1.2 & Verify bootloader configurations are immutable in production releases. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
444 & OWASP ISVS & test & 3.1.1 & Verify that the bootloader does not allow code to be loaded from arbitrary locations. Locations include both storage (SD, USB, etc.) and network locations (over TCP/IP). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
445 & OWASP ISVS & test & 2.4.6 & Verify the cryptographic libraries used are certified to be compliant with a recognized cryptographic security standard. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
446 & OWASP ISVS & test & 2.4.5 & Verify that cryptographic primitives used by the device are provided by dedicated security chips. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
447 & OWASP ISVS & test & 2.4.4 & Verify that cryptographic secrets used by the device are stored securely by leveraging functionality provided by dedicated security chips. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
448 & OWASP ISVS & test & 2.4.3 & Verify secure sources of randomness are provided by the operating system and/or hardware for all security needs. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
449 & OWASP ISVS & test & 2.4.2 & Verify proper use of cryptography. Only standard and strong algorithms should be used, with adequate key size and secure implementations. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
450 & OWASP ISVS & test & 2.4.1 & Verify cryptographic secrets are unique per device. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
451 & OWASP ISVS & test & 2.3.4 & Verify that sensitive information maintained in memory is overwritten with zeros as soon as it is no longer required. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
452 & OWASP ISVS & test & 2.3.3 & Verify that in case a device is decommissioned, or the owner changes, it is marked as such for auditable purposes in a centrally managed database in the ecosystem. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
453 & OWASP ISVS & test & 2.3.2 & Verify that in case a device is decommissioned, or in case the owner changes, all sensitive information such as PII data and credentials can be removed from the device. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
454 & OWASP ISVS & test & 2.3.1 & Verify that sensitive information such as personal identifiable information (PII) used by the device is stored securely on the device. Protection can include encryption against data leakage, and hashing or integrity checking against unauthorized modification. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
455 & OWASP ISVS & test & 2.2.5 & Verify device debug capabilities can only be accessed by approved staff (e.g. support and engineering teams) and verify that access is monitored/logged. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
456 & OWASP ISVS & test & 2.2.4 & Verify that ownership is validated upon registration and as part of decommissioning when devices move across accounts. e.g. Device reselling, leasing, and renting. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
457 & OWASP ISVS & test & 2.2.3 & Verify that devices enforce the concept of least privilege by limiting applications and services that run as root or administrator. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
458 & OWASP ISVS & test & 2.2.2 & Verify that IoT system accounts across users, services and devices share a common authorization framework. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
459 & OWASP ISVS & test & 2.2.1 & Verify that sensitive information such as personal identifiable information (PII) and API keys are stored securely using encryption to protect from data leakage, and integrity checking to protect against unauthorized modification. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
460 & OWASP ISVS & test & 2.1.6 & Verify good password policies are enforced throughout the IoT ecosystem by disallowing hardcoded passwords and provisioning duplicate identities or passwords across devices. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
461 & OWASP ISVS & test & 2.1.5 & Verify certificate based authentication is preferred over password based authentication within the IoT ecosystem. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
462 & OWASP ISVS & test & 2.1.4 & Verify that user, services, and device authentication schemes share a common framework centrally managed in the IoT ecosystem. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
463 & OWASP ISVS & test & 2.1.3 & Verify strong user and device authentication is enforced across the IoT ecosystem. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
464 & OWASP ISVS & test & 2.1.2 & Verify that all connected devices within the IoT ecosystem can be uniquely identified including connected to the cloud, hubs, as well as to other devices (sensors). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
465 & OWASP ISVS & test & 2.1.1 & Verify that all forms of users and accounts in the IoT ecosystem can be uniquely identified. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
466 & OWASP ISVS & test & 1.3.9 & Verify packages are compiled with Position Independent Executable (PIE). e.g. -fPIE & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
467 & OWASP ISVS & test & 1.3.8 & Verify packages are compiled with No eXecute (NX) or Data Execution Protection (DEP). e.g. -z,noexecstack & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
468 & OWASP ISVS & test & 1.3.7 & Verify packages are compiled with Object Size Checking (OSC). e.g. -D\_FORTIFY\_SOURCE=2 & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
469 & OWASP ISVS & test & 1.3.6 & Verify that compilers, version control clients, development utilities, and software development kits are analyzed and monitored for tampering, trojans, or malicious code & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
470 & OWASP ISVS & test & 1.3.5 & Verify build pipelines only perform builds of source code maintained in version control systems. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
471 & OWASP ISVS & test & 1.3.4 & Verify packages are downloaded and built from trusted sources. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
472 & OWASP ISVS & test & 1.3.3 & Verify that use of banned C/C++ functions (i.e. memcpy, strcpy, etc.) are replaced with safe equivalents functions (e.g. Safe C). & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
473 & OWASP ISVS & test & 1.3.2 & Verify GPL based firmware has its source code published and that no sensitive or proprietary information is accidentally included in the process. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
474 & OWASP ISVS & test & 1.3.15 & Verify that embedded applications are not susceptible to OS command injection by performing input validation and escaping of parameters within firmware code, shell command wrappers, and scripts. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
475 & OWASP ISVS & test & 1.3.14 & Verify that debug information does not contain sensitive information, such as PII, credentials or cryptographic material. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
476 & OWASP ISVS & test & 1.3.13 & Verify that debug and release firmware images are signed using different keys. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
477 & OWASP ISVS & test & 1.3.12 & Verify release builds do not contain debug code or privileged diagnostic functionality. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
478 & OWASP ISVS & test & 1.3.11 & Verify packages are compiled with read-only relocation (RELRO). e.g. -Wl,-z,relro & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
479 & OWASP ISVS & test & 1.3.10 & Verify packages are compiled with Stack Smashing Protector (SSP). e.g. -fstack-protector-all & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
480 & OWASP ISVS & test & 1.3.1 & Verify that each application in the ecosystem is built using a secure and repeatable build environment. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
481 & OWASP ISVS & test & 1.2.9 & Verify debug paths and traces are depopulated from production PCBs. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & True \\ \hline 
482 & OWASP ISVS & test & 1.2.8 & Verify third-party code and components are analyzed using static analysis tools to ensure backdoors are not introduced. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
483 & OWASP ISVS & test & 1.2.7 & Verify that code integrity protection mechanisms are enabled and locked in hardware before shipping the device to customers. For example, ensure secure boot is enabled and the boot configuration locked. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
484 & OWASP ISVS & test & 1.2.6 & Verify that devices are provisioned with a cryptographic root of trust that is hardware-based and immutable. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
485 & OWASP ISVS & test & 1.2.5 & Verify debug capabilities in FPGAs are disabled. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
486 & OWASP ISVS & test & 1.2.4 & Verify that access to debugging interfaces (e.g. JTAG, SWD) is disabled or protected before shipping the device. Processors may refer to this as code protection, read back protection, CodeGuard, or access port protection. & False & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
487 & OWASP ISVS & test & 1.2.3 & Verify the device is released with firmware and configuration appropriate for a release build (as opposed to debug versions). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
488 & OWASP ISVS & test & 1.2.2 & Verify that potential areas of risk that come with the use of third-party and open-source software have been identified and that actions to mitigate such risks have been taken. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
489 & OWASP ISVS & test & 1.2.1 & Verify that each application (including firmware) in the ecosystem maintains a software bill of materials (SBOM) cataloging third-party components, versioning, and published vulnerabilities. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
490 & OWASP ISVS & test & 1.1.7 & Verify that users and relevant stakeholders are notified when vulnerabilities are identified through established communication channels (website, e-mail ...). & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
491 & OWASP ISVS & test & 1.1.6 & Verify that a responsible disclosure policy has been established and that it is easily found on the company website. Ensure that the policy provides a clear overview on how vulnerabilities can be communicated securely and how they'll be followed up on. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & False & False \\ \hline 
492 & OWASP ISVS & test & 1.1.5 & Verify that security controls are enforced server-side and that data and instructions are not blindly trusted by server-side components. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
493 & OWASP ISVS & test & 1.1.4 & Verify that the location where sensitive data is stored in the ecosystem is clearly identified and separated from unprivileged storage locations. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
494 & OWASP ISVS & test & 1.1.3 & Verify that sensitive information and security critical actions have been identified and documented. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
495 & OWASP ISVS & test & 1.1.2 & Verify that all components and communication channels in the IoT application's ecosystem have been identified and are known to be needed. Remove or disable any that aren't necessary. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
496 & OWASP ISVS & test & 1.1.1 & Verify that all applications in the IoT ecosystem are developed with a level of security that is in line with the security criticality of the application. & True & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & \textit{NULL} & True & True \\ \hline 
 \end{longtable}
